\section{Introduction}
\label{sec:introduction}
\subsection{A Game of Make-Believe}
\emph{Sanguine Dreams} is a live-action role-playing game where we as players get to 
step outside of ourselves for a few hours each week and portray a character, one whose 
outlook and history is likely far different from our own.  Taking place within White 
Wolf's \emph{World of Darkness} setting, our troupe focuses on the political maneuverings 
and rich social interactions between characters, much like in a murder mystery or British drama.

Each of the characters presented in our weekly game are vampires, largely adhering to the 
societal norms presented in White Wolf's books, with matching game mechanics. In the more 
than fifteen years since \emph{Vampire: the Masquerade, Revised} was released, games such 
as ours have identified aspects which need to be altered or adjusted to suit their 
particular group's play-style.  Combined with the difficulty of obtaining the long
out-of-print rule books, the players and Storytellers of Sanguine Dreams have come together 
to create this document, detailing our vision of \emph{Vampire} and to make an introduction 
to the setting and game we love as straightforward as possible for our new and veteran players. 

We in no way desire to infringe on the copyrights of \emph{White Wolf} or its parent 
company \emph{CCP North America}, and highly encourage our players to purchase their products 
where available; far more information can be found within the guides, rulebooks, and novels 
they have published than we could ever present in this collection, particularly as relates to the 
setting and history of the world in which our game takes place.

As the \emph{World of Darkness} is a mature setting wherein which the themes of loss, 
terror, violence, seduction, and betrayal may take place, our game is only open to 
adults over the age of eighteen except by explicit parental permission.

While the stories that develop are largely shaped by the players, the small Storytelling 
staff presents the world at large and all non-player characters in the world.  It is their 
job to help new players, adjudicate rules, provide the proper mood and setting, and 
encourage a healthy and productive gaming environment.  As a player you should always feel 
free to speak your mind with them, and to write down any complaints or concerns so they 
can be addressed.

There are many rules and game mechanics in these pages, but the most important rules to 
which every player must adhere are as follows:

\begin{description}
	\item[No Touching:] Do not touch other players in ways they do not like or do not find 
	appropriate.  Similarly, if an interaction makes you feel uncomfortable, make it known 
	so there is no confusion.  Vampires are often portrayed as sensual creatures but it is 
	essential to respect and value the personal feelings of the other players, far beyond 
	the wants and habits yourself or the character you play.
	\item[No Stunting:] Do not risk injury or damage to yourself or property by 
	running, jumping, climbing, sliding, or otherwise taking gambles with your person.  Vampires 
	may be immortal monsters but we as players certainly are not, and need to take into consideration 
	our limits as well as those of others, including the sites at which we play which may have their 
	own rules and regulations regarding conduct or behavior.
	\item[No Weapons:] While some characters may be armed to the teeth, there is no excuse for 
	bringing any sort of weapon to a game site, including realistic-looking props.  Empty holsters and 
	sheathes to simulate having a weapon may be approved by the Storytellers, but please ask permission 
	before bringing or wearing them, for everyone's comfort and safety.
	\item[No Drugs or Alcohol:] Pretending to be a vampire is often difficult enough while sober, 
	please do not attempt it while in an altered state.  We play on private and public grounds 
	where often the consumption of alcohol and drugs are prohibited, prescription or otherwise.  
	For your safety and that of other players, those under the influence will be asked to leave the 
	game site.
	\item[It's Only a Game:] Vampires are not real.  Nothing that happens to your character is 
	real.  If something befalls your character it does not reflect on you as a person; it is merely 
	a continuation of a story for which there are thirty or more authors, and not every chapter 
	ends how you expect it to.  There is no reason to be long upset about what happens at game, as 
	we have built a positive and friendly out-of-character environment in which to enjoy this hobby.
	\item[Be Respectful of Others:] This should go without saying.  \emph{Sanguine Dreams} is a 
	collective of individuals who have come together to have fun and role-play.  Be mindful of 
	others' feelings and respectful of their boundaries, personal space, and attitude.  Remember 
	that everyone comes to the game for their own reasons, with their own aims, but foremost everyone 
	is here for a good time.  Work to facilitate a positive gaming environment for everyone.  If a 
	conflict arises, bring it to the attention of the Storytellers so they may mediate a resolution.
	\item[It's Everyone's Game:] The Storytellers may have helped craft the world and the 
	situations our characters find themselves in, but it is the playerbase that has made this game 
	a thriving success for more than a decade.  No one contributor is more important than any other 
	and everyone should have equal chance to participate, enjoy, and add to this rich story.
	\item[Have Fun:] We all know people who get too into games and are caught up on ``winning'' 
	and ``losing,'' as if every encounter bore the weight of the world.  In collaborative 
	storytelling, there truly aren't winners and losers---this is a group effort.  Having character 
	goals, diving into their mindset, and exploring their stories are the best ways to stave off 
	boredom, but if you need specific suggestions, please talk to your fellow players and to the 
	Storytellers---doubtlessly a solution will arise that is exciting while not detrimental to others' 
	enjoyment as well.  We're all here for entertainment and friendship.
\end{description}

\subsubsection{Other Resources}
In addition to the rich community of players and Storytellers we have built in the formation of 
\emph{Sanguine Dreams} and its website found at \emph{http://sanguinerpg.com}, the many books published 
by White Wolf are invaluable resources for delving into the themes, moods, and atmosphere of the 
World of Darkness.  The rules in this specific volume take precedence over those appearing in others, 
but we highly encourage the perusal (and purchase) of the books listed below, and many others, for 
anyone wishing a deeper understanding of the setting, and the basis upon which we have built this rules 
document.

\begin{itemize}
	\item \textbf{Laws of the Night: Revised} --- the primary rulebook which inspired this 
	tome, it is the backbone of live-action Vampire role-playing.
	\item \textbf{Guide to the Camarilla} (table-top) --- there is no better book to understand 
	the rich traditions and internal mechanizations of this global society.
	\item \textbf{Council of Primogen} (2nd edition, table-top) --- the politics and underpinnings 
	of the Primogen Council are often a mystery to new players, and this book illustrates how various 
	Clans choose their Primogen, what makes them effective, and how they conduct business.
	\item Each of the revised edition \textbf{Clanbooks} --- Every Clan has a single volume dedicated 
	entirely to its history, internal structures, politics, and motivations.  These are absolutely 
	invaluable resources for anyone wishing to dive deeper into the culture and organization of their 
	Clan.
	\item \textbf{The Prince's Primer} (2nd edition) --- so, you want to be Prince? \\
\end{itemize}

\noindent All of the rules for play used by \emph{Sanguine Dreams} are contained within this book 
and the additional guides we have made available for player use, save by Storyteller fiat or necessity.  
Other supplements we have created and which are available at game include:

\begin{itemize}
	\item \textbf{The World Uncovered} --- providing an overview of the world in general, the 
	United States in particular, and the Bay Area in specific, this guide details the setting of our 
	game, as seen through a vampire's eyes.
	\item \textbf{Mortal Manipulations} --- how the \emph{Influence} and \emph{Contacts} Backgrounds can 
	be used to great effect, effectively a game within a game.
	\item \textbf{Crimson Terrors} --- the definitive guide to the Disciplines of \emph{Thaumaturgy} 
	and \emph{Necromancy}, as well as the Clans that practice them.
\end{itemize}

\subsubsection{The Two Golden Rules}
\begin{description}
	\item[Player Consensus:] \hfill \\ 
	If all players involved in a scene agree upon a resolution or effect that 
	is not contrary to the spirit of the game's rules or setting, they may at their 
	own discretion disregard or alter the rules to better enhance role-play for 
	that specific scene. \\
	\item[The Storyteller's Prerogative:] \hfill \\
	The Storytellers may interpret, modify, alter, or disregard any and all rules 
	for the sake of the flow of a scene, the quality of the story, or for other 
	necessity.  All such rulings or changes last for the scene in question only.
\end{description}

\subsection{A World of Shadows}
Imagine the world we know, but far darker, malicious, and selfish.  Philanthropy is a 
foreign concept to most people, who each focus far more on their day-to-day existence and the 
threats others pose than the general welfare of their society.  Violence is commonplace in 
the news, when it is reported at all, and people go missing far more often than we would be 
comfortable with.

The primary reason for this state of decay is that, for the past 500 years and even longer, 
vampires have been molding society, whether consciously or just by their very presence as they 
move through the shadows.  These lords of the night have ruled humanity from their secretive 
havens, keeping their existence an almost impermeable secret while continuing to direct and shape 
its future.

Of the many vampire Clans, several have banded together for mutual aid and support, no matter how 
tenuous those alliances may be.  Named ``the Camarilla,'' this worldwide structure of vampires, 
calling themselves ``kindred,'' don the fa\c{c}ade and trappings of civility and publicly strive 
to be as humane and just as possible, sometimes denying their more base, brutal natures.  Standing 
opposed to the Camarilla are its enemies:  those in the religious organization called ``the Sabbat,'' 
the young Anarch movement striving to define its own place, and those few Clans who have decided to 
stand apart from any greater political affiliation, doing business with whomever they so choose.

\emph{Sanguine Dreams} is a Camarilla-based game, meaning the overwhelming majority of 
characters approved for play will be loyal to that Sect and to its tenets, more or less.  
Other vampires outside of Sonoma County and outside the Camarilla do exist, but every 
kindred (should) know the dangers of striking a bargain with \emph{others}.  More 
information regarding other Clans and the Camarilla can be found in their respective 
chapters.

Our game focuses on the political and interpersonal nature of vampire society, the court 
intrigue and social maneuvering of creatures who have spent decades perfecting their craft.  
While the concept of violence, that looming threat and horror of the setting, abounds in our 
week to week game, actual character-on-character physical combat is low.  Characters designed 
to be purely muscle or otherwise physically dangerous may be bored or lack enough ``excitement'' 
to hold their interest---ours is a social game, like the great royal courts of old.

Specific notes on the setting, time-frame, and details about the world at large can be found on our 
website, which will explain in detail the current chronicle environment.

\section{The CAG-SSU Club}
Thanks to the hard work and diligence shown by many of our Sonoma State University student players, 
\emph{Sanguine Dreams} hosts most of its games at the Rohnert Park university campus.  This was a 
hard-won privilege and there are specific rules and guidelines that must be followed if we are to 
maintain our positive relationship with the college administration.  The full club charter as well 
as membership roster can be found in a special forum at \emph{https://sanguinerpg.com}

Under the auspice of the \emph{Collaborative Association of Gamers and Story-tellers at Sonoma State 
University} (CAG-SSU) club, we are able to reserve rooms and legally hold our events at the college.  
That means we are bound by their constitution as well as general campus rules.  As a summary, all 
players, whether they are students or not, must abide by the following at all times:

\begin{itemize}
	\item On-campus games must be scheduled through the club, and players should not explore or enter 
	classrooms or other campus locations not designated and reserved by the club.  Barring special events 
	this normally means the Ives Hall basement level, rooms 78 and 44.
	\item No smoking and absolutely no drinking or drugs while on campus.  Self-explanatory, this rule is 
	strongly enforced by both campus policy and state law.
	\item No weapons of any kind.  We play on a public university and the merest presence or suggestion of 
	weapons -- even realistic, non-functional props can result in the most unfortunate of circumstances, the 
	least of which 	being our removal from SSU.
	\item Clean up the game site.  If there is trash discovered at our game site after we have left, even if 
	it is not from our group, we will be held responsible for it.  That means picking up cigarette butts, 
	foodstuffs, and other trash.  SSU endeavors to remain a clean campus and we must help accomplish that goal 
	if we are to continue playing there.
	\item The club President is the final authority on all matters relating to using SSU as a game site.  If 
	there is confusion or questions relating to a school or club rule, they will make the final decision.
	\item The voting body of CAG-SSU is made up of current, full-time SSU students.  Every player should make 
	an effort to recruit more members, not just for \emph{Sanguine Dreams} but for the club in general, 
	which helps promote gaming of all kinds across the student body.  Without active students as members and 
	leaders of the club, we will lose the ability to play on campus.
\end{itemize}