\section{Merits and Flaws}
\label{sec:merits}
One of the most versatile aspects of character creation, Merits and Flaws 
represent those unique advantages and disadvantages which help distinguish 
one character from another.  When creating your character you are limited 
to a total of seven points of Merits and only receive Free Traits for the 
first seven points of Flaws, making your selections very important.  While 
most Merits and Flaws have mechanical effects, many have social repercussions 
as well which facilitate greater role-play.  Additionally it is exceedingly 
difficult to develop Merits and Flaws after character creation, and plans to 
do so must be discussed with Storytellers.

With the wide array of \emph{Vampire} sourcebooks available there are many places 
to find Merits and Flaws for your character.  Here we have compiled a master list 
of every Merit and Flaw available in \emph{Sanguine Dreams} along with a brief 
description of what the Merit or Flaw provides.  In several cases the point values 
or effects of specific Merits and Flaws have been adjusted from the source material; 
use the values and description listed below.  If necessary more information is 
available in the indicated sourcebook. Some \emph{Sanguine Dreams}-specific Merits and 
Flaws are accessible to certain Clans only, and have been marked as such.

No Flaw will give characters a mechanical edge over others; this is represented 
most specifically in cases such as \emph{Blind} and \emph{Deaf} not making a 
character immune to the Discipline of Dominate.  When there is a doubt as to the 
effects of particular Merits or Flaws, please see a Storyteller.

Only one Merit may be used per contender in a challenge, and it must be declared 
before the challenge is thrown. All relevant Flaws apply and must similarly be 
declared.  No characters may purchase Merits or Flaws found in Clanbooks not their 
own, and no Camarilla kindred may have entries from the Sabbat or Anarch guides 
without specific Storyteller approval. \\

\begin{minipage}{0.5\textwidth}
   \begin{flushleft}
	\emph{SD} --- Sanguine Dreams-specific \\
	\emph{LotN} --- Laws of the Night \\
	\emph{CG} --- Guide to the Camarilla \\
	\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
   \begin{flushleft}
	\emph{Clan} --- Clanbook \emph{(Clan)} \\
	\emph{Sabbat} --- Guide to the Sabbat \\
	\emph{Anarch} --- Guide to the Anarchs \\
	\end{flushleft}
\end{minipage}

\subsection{Physical Merits}
\begin{description}
	\item[Ability Aptitude] (SD, 1):  Naturally proficient at some task, 
	you gain a +2 bonus on ties for a single non-combat, non-Discipline Ability. 
	For Abilities which require a focus such as \emph{Crafts} or \emph{Expression}, 
	this merit only applies to one specific focus as they are treated as different 
	Abilities.
	\item[Acute Sense] (LotN 112, 1):  Gifted with enhanced senses, gain a +1 
	bonus on perception or investigative challenges using that sense.
	\item[Ambidextrous] (LotN 113, 1):  Suffer no trait penalties when using an item 
	with your non-dominant hand (normally -2 otherwise).
	\item[Blush of Health] (LotN 113, 2):  Naturally rosy and warm to the touch, 
	this Merit negates 2 points of penalty for having low Humanity when dealing 
	with mortals. Stacks with the ability to spend Blood for this effect.
	\item[Bruiser] (CG 24, 1):  Gain a +1 Social bonus when intimidating someone face to face.
	\item[Catlike Balance] (LotN 113, 1):  Gain +2 traits when testing to maintain 
	your physical balance.
	\item[Daredevil] (LotN 113, 3):  Gain a +1 Physical bonus trait when engaging in 
	exceptionally risky or suicidal behavior, at Storyteller discretion.
	\item[Deadened Nerves] (Malkavian 65, 4):  Cursed with very little tactile 
	sense, you do not feel pain as others do.  You neither suffer the drawbacks 
	from being Bruised nor need to risk two traits when Wounded.
	\item[Drug Resistance] (SD, 2):  \emph{Followers of Set only.}  You are 
	highly resistant to mundane intoxicants and narcotics and suffer no penalties for 
	having either in your system.  Not compatible with \emph{Addiction}.
	\item[Early Riser] (Sabbat 72, 1):  You always wake at nightfall, regardless of 
	your Morality rating.
	\item[Eat Food] (LotN 113, 1):  Unlike other kindred you may stomach food 
	and drink for up to an hour before needing to expel it.
	\item[Efficient Digestion] (LotN 113, 3):  For every two blood traits you 
	ingest you may add three to your blood pool.
	\item[Enchanting Voice] (LotN 113, 2):  Your melodious voice grants you a +2 bonus 
	on ties in Social challenges where you are speaking in someone's presence.
	\item[Foul Blood] (Nosferatu 71, 3):  Any who feed from you must win a Simple 
	test or be nauseated for the next scene or hour, suffering -1 to all challenges.  This 
	Merit may make creating ghouls or Blood Bonds difficult.
	\item[Friendly Face] (CG 24, 1):  Gain a +1 bonus to Social challenges when interacting 
	in a friendly way towards a stranger in their presence.
	\item[Gaping Maw] (Nosferatu 71, 2):  Each turn you may drain a subject of four 
	Blood instead of the normal three.  Not compatible with \emph{Blunt Fangs}.
	\item[Huge Size] (LotN 113, 4):  Hulking over other people you are not likely 
	to be missed.  Gain an additional Bruised health level.
	\item[Lizard Limbs] (Nosferatu 70, 1):  By spending a Blood and Willpower you 
	can shed one of your limbs, granting you the negative trait \emph{Lame} which 
	persists until it grows back.  It can be healed as if it were a point of 
	Aggravated damage.
	\item[Long Fingers] (Nosferatu 70, 1):  Gain a +1 trait bonus in all non-combat 
	challenges of fine dexterity such as lock picking.
	\item[Oversized Fangs] (Nosferatu 70, 1):  After establishing a grapple gain 
	a bonus of +2 on biting attacks.  Your bite does an extra level of damage. 
	Gain the \emph{Permanent Fangs} Flaw for no points.
	\item[Pain Tolerance] (Tzimisce 69, 2):  Ignore the effects of the Bruised health 
	level.
	\item[Patagia] (Nosferatu 72, 4):  You may glide on leathery wings at walking 
	speed when aided by a strong wind.  This is an obvious breach of the the Masquerade.
	\item[Piscine] (Nosferatu 71, 1):  At home underwater, gain a bonus of +1 on 
	swimming or underwater-related challenges.
	\item[Poisonous Bite] (SD, 1 or 3):  \emph{Followers of Set only.}  You have 
	developed poison glands which may be used to attack your prey.  Your poison is immediately 
	lethal to all mortals though kindred and other supernaturals are unaffected.  For one point 
	this poison always injects when you bite, making feeding difficult.  For three points 
	you can selectively choose whether or not to inject the poison.
	\item[Projectile Vomiting] (Nosferatu 71, 2):  Also including the benefits of 
	\emph{Eat Food}, you may direct your vomit at a nearby target, though this attack 
	does not deal damage.  Retest with \emph{Athletics}.
	\item[Rugged Bad Looks] (Nosferatu 72, 4):  When fully bundled and only seen 
	for a moment you could pass as human, from a distance.  This is the most attractive 
	any Nosferatu is able to get without the aid of Disciplines.
	\item[Slimy] (Nosferatu 71, 1):  Gain an extra Healthy health level for resisting 
	fire damage and +2 traits when resisting a grapple.
	\item[Tough Hide] (Nosferatu 71, 2):  Gain an additional Bruised health level.
\end{description}

\subsection{Physical Flaws}
\begin{description}
	\item[Addiction] (LotN 114, 3):  While under the effects of your chosen drug you 
	suffer a Negative trait.  When you are off it, suffer a different one.
	\item[Anosmia] (Nosferatu 73, 2):  Lose all tests relating to smell or taste, and 
	you probably smell awful.  Even \emph{Heightened Senses} cannot help you.
	\item[Bad Sight] (LotN 114, 2):  Suffer a -2 trait penalty on all vision and ranged 
	combat challenges.  This Flaw is not correctable with glasses.
	\item[Blind] (LotN 116, 6):  You always suffer the effects of being in Darkness (see 
	page~\pageref{sec:challenges}) and fail any challenge requiring sight.  You are not 
	immune to \emph{Dominate}.
	\item[Blunt Fangs] (Nosferatu 72, 1):  Grants an extra retest to any who are resisting your 
	bite.  You must make a new test every turn to continue feeding.  Deal one Lethal damage per 
	Blood trait drawn in this way.
	\item[Contagious] (Nosferatu 74, 5):  Dealing with so many dead bodies has made you 
	highly infectious to mortals; any who interact with you must win a Simple test or fall 
	victim to your plague, testing again in one week's time to attempt to recover.
	\item[Deaf] (LotN 115, 4):  You are automatically Surprised when attacked from behind 
	and fail all auditory tests.  This Flaw does not make you immune to \emph{Dominate}.
	\item[Deformity] (LotN 114, 3):  A twisted and deformed body causes you to have a -1 
	penalty on all Physical and -2 on all Social challenges.
	\item[Disease Carrier] (LotN 115, 4):  Choose a virulent, infectious disease with 
	Storyteller approval.  Spend an extra Blood upon waking to avoid suffering from your 
	disease that night.  Any who feed from you must win or tie a Simple test to avoid 
	contracting the disease temporarily.
	\item[Disfigured] (LotN 114, 2):  You may not take any Appearance-based Social traits 
	and suffer a -2 penalty to all non-intimidating Social challenges.
	\item[Dulled Bite] (CG 24, 2):  As \emph{Blunt Fangs} without the additional damage effect.
	\item[Fangless] (Anarch 115, 2):  You do not have fangs and must find another way to 
	feed.
	\item[Flesh of the Corpse] (LotN 115, 2):  Each wound you heal punishes you with the 
	Negative Trait \emph{Repugnant} until you sleep.
	\item[Forked Tongue] (SD, 2):  \emph{Followers of Set only.}  Your tongue is 
	forked, making speaking intelligibly difficult and perhaps posing a threat to the Masquerade.  
	This Flaw does not mimic any of the benefits of \emph{Tongue of the Asp}.
	\item[Glowing Eyes] (CG 25, 2):  Your bright eyes grant you \emph{Bestial} and 
	\emph{Repugnant} and are an obvious breach of the Masquerade.
	\item[Hard of Hearing] (LotN 113, 1):  Suffer a -2 penalty on hearing-based tests.
	\item[Inbred] (Giovanni 78, 1-5):  Suffer Social and Physical penalties due to your 
	disfigurement.  See the Giovanni Clanbook for more information.
	\item[Infectious Bite] (LotN 114, 3):  Choose a virulent disease that lives in your system. 
	Win or tie a Simple test after feeding or you transmit your disease to your victim. You 
	cannot lick closed wounds you make while feeding.
	\item[Infertile Vitae] (Sabbat 73, 5):  You are incapable of siring childer, creating 
	ghouls, or blood bonding others.
	\item[Lame] (LotN 115, 3):  You may only take 1 step per Combat action.
	\item[Lazy] (Sabbat 72, 3):  Suffer a -1 trait penalty on all spontaneous actions.
	\item[Monstrous] (LotN 115, 3):  Mechanically you possess the Nosferatu Clan disadvantage, 
	though no true Nosferatu would confuse you for one of their own.
	\item[Mute] (LotN 115, 4):  You cannot speak or make yourself understood vocally.
	\item[One Eye] (LotN 114, 2):  -2 traits on all tests where depth perception would 
	aid you, such as ranged combat.
	\item[Open Wound] (SD, 2 or 5):  You have one or more wounds that refuse to 
	heal and continually seep blood, costing you one Blood trait at the start of gather.  For 
	five points this Flaw also includes the penalties of \emph{Permanent Wound} and grants a 
	corresponding Negative Social or Physical trait.
	\item[Parasitic Infestation] (Nosferatu 73, 2):  Due to the insects and parasites 
	crawling in and through you, lose 4 Blood at the start of each gather and suffer 
	-1 to all Self-Control/Instinct tests.
	\item[Permanent Wound] (LotN 115, 3):  Wake each night injured through the first 
	Wounded health level.
	\item[Permanent Fangs] (CG 25, 3):  Your fangs do not retract normally, granting you 
	\emph{Bestial} and potentially threatening the Masquerade.
	\item[Putrescent] (Nosferatu 74, 4):  When you take damage win or tie a Simple test 
	to avoid it becoming aggravated due to your advanced decay.  You stink like a truly 
	rotten corpse as per \emph{Smell of the Grave}.
	\item[Revenant Weakness] (Tzimisce 70, 3):  Suffer the additional disadvantage of the 
	revenant family from which you hail.
	\item[Scarface] (Tzimisce 70, 2-4):  Gain additional physical and social drawbacks based 
	on the points taken.  See the Tzimisce Clanbook for specifics.
	\item[Short] (LotN 113, 1):  Child-sized, you may only take 2 steps per Combat action.
	\item[Slow Healing] (LotN 115, 3):  Double all Blood costs for healing.
	\item[Smell of the Grave] (LotN 114, 1):  Suffer a -1 trait penalty on all interactions 
	with mortals due to the stench of death that surrounds you.
	\item[Thin Blood] (LotN 115, 4):  All blood costs are doubled, you cannot blood bond 
	others, and to embrace another you must win an extra Simple test.
	\item[Vulnerability to Silver] (Sabbat 72, 2):  Take a -1 trait penalty when touching 
	silver and suffer aggravated wounds when attacked by a silver weapon.
	\item[Withered Leg] (Nosferatu 73, 3):  Gain \emph{Lame x3} and fail any challenge 
	requiring two good legs.
\end{description}

\subsection{Social Merits}
\begin{description}
	\item[Blaz\'{e}] (SD, 3):  \emph{Toreador only.}  You are not easily impressed by others' creative 
	endeavors.  Once per night you may gain a retest when defending against Presence.
	\item[Clan Friendship] (SD, 3):  Owing to many past deeds done to help a particular Clan you 
	gain a +2 bonus on non-intimidating Social challenges against members of that Clan, who should be 
	predisposed to aid you in your endeavors.  This Merit may be lost permanently if you don't 
	continue to promote their interests.
	\item[Debt of Gratitude] (LotN 118, 1 to 5):  An older kindred owes you a Boon; normally a trivial or 
	minor.  Details of the Boon and your benefactor should be worked out with the Storytellers.
	\item[Dynamic Personality] (Brujah 68, 5):  You are a natural socialite and gain two dots of 
	\emph{Allies}, \emph{Contacts}, or \emph{Retainers} per XP or Free Trait spent.
	\item[Mortal Double] (SD, 3):  You possess a \emph{Retainer} who looks exactly like you.  Perhaps 
	they are a mortal twin or it is a freak coincidence.  This individual may help you with preserving 
	your status in the mortal realm, helping hide your vampiric nature.  They must know everything about 
	your night-to-night activities however, and must both be a good actor and well-treated.  If they 
	aren't made a ghoul physical differences will soon appear as they age.
	\item[Natural Leader] (LotN 118, 1):  Gain +2 traits on Social challenges that are retested with the 
	\emph{Leadership} ability.
	\item[Paragon] (Ventrue 77, 6):  Your maximum cap for a single Background or Influence is 
	increased by one.
	\item[Prestigious Sire] (LotN 118, 2):  Granting no mechanical benefits, you are more likely 
	to be favored over others who have the same amount of Status, owing to your impressive lineage.
	\item[Quiet Heart] (SD, 4):  Not easily swayed, gain +3 traits when resisting 
	\emph{Presence} and other emotion-altering Disciplines.  Does not aid against \emph{Dominate}.
	\item[Reptile Buddy] (Nosferatu 71, 3):  You have cultivated a powerful alligator friend, 
	whose stats are available in the Nosferatu Clanbook.
	\item[Sanctity] (Sabbat 73, 2):  An aura of innocence surrounds you, granting you +2 traits 
	on non-aggressive Social challenges and often affords you lighter punishments for your 
	transgressions.
	\item[Status] (SD, 1-5):  A powerful kindred has given you Patronage Status.  Each point of 
	this Merit represents up to three Status your patron has, and requires a compelling background 
	approved by the Storytellers.  Note that this Status may be permanently lost if you do not live 
	up to your reputation.
\end{description}

\subsection{Social Flaws}
\begin{description}
	\item[Anachronism] (SD, 1):  Embraced many decades ago, you cannot cope with or 
	understand modern fashion, technology, or social progress of any kind.  You know the world 
	has changed, but always assert that it should not have.  You cannot possess the \emph{Computers} 
	Ability and other Abilities may be limited in their usefulness or relevance.
	\item[Bound to the Council] (Tremere 67, 3):  As punishment for past transgressions you have 
	been more strictly bound to the Clan.  Spend a Willpower to willfully violate the commands of 
	the Tremere hierarchy.  Other Tremere are unlikely to trust you.
	\item[Clan Enmity] (SD, 2):  Owing to many past deeds done to hinder a particular Clan you 
	suffer a -2 penalty on Social challenges against members of that Clan, who should be predisposed 
	to distrust you and hinder your endeavors.
	\item[Dark Secret] (LotN 119, 1):  There is a dark element of your history that, if discovered 
	could result in you losing Status, or worse.
	\item[Double Betrayer] (Tremere 67, 4):  Not only did you betray your oaths and join the Sabbat, 
	you then betrayed those oaths and came back.  Suffer a -2 penalty on all Social or Mental challenges 
	against other Tremere and you likely also possess \emph{Bound to the Council}.  Gain \emph{Dark Secret} 
	for no points.
	\item[Enemy] (LotN 119, 1-5):  A powerful group of enemies work to undermine your efforts and 
	may go so far as to threaten or take your life.
	\item[Enemy Brood] (Nosferatu 73, 3):  As per the \emph{Hunted} Flaw save those after you are 
	other Nosferatu, thirsting for revenge for past misdeeds.
	\item[Hunted] (LotN 119, 4):  A powerful hunter or group knows your location and is actively 
	trying to end your existence.
	\item[Infamous Autarkis] (Nosferatu 72, 1):  Something in your or your sire's past is so 
	abhorrent that neither the Camarilla nor Sabbat will accept you into their societies.
	\item[Infamous Sire] (LotN 119, 1):  Suffering no mechanical penalties, you are less likely 
	to be seen as equal to others who have the same amount of Status, owing to your notorious lineage.
	\item[Mistaken Identity] (LotN 119, 1-5):  You bear a remarkable resemblance to a powerful 
	and noteworthy kindred, which causes you no end of grief, threats, and derision.
	\item[Necrophile] (Nosferatu 73, 3):  Your haven is filled with the dead, whose company you 
	enjoy.  Visitors are disgusted with you.
	\item[Obvious Predator] (Brujah 69, 2):  Your Beast rides high toward the surface in every 
	encounter.  Suffer -2 traits on non-intimidating Social challenges with mortals.
	\item[Prestation Debt] (LotN 118, 1 to 5):  You owe an older kindred a Boon; normally a trivial or 
	minor.  Details of the Boon should be worked out with the Storytellers.
	\item[Probationary Sect Member] (LotN 119, 4):  Newly-accepted into the Camarilla from either 
	another Sect or independent alignment, you are always considered to have at most one Status.
	\item[Recruitment Target] (SD, 2):  The Sabbat wants you, and they want you bad.  Every effort 
	is being made to recruit you, and they always show up at the worst possible time.  Work with the 
	Storytellers to develop why.
	\item[Sire's Resentment] (LotN 119, 1):  A falling out with your sire has caused them to 
	work to ensure that other potent members of the Sect will not aid you.  You may not possess 
	the Mentor Background.
	\item[Special Responsibility] (Sabbat 73, 1):  Charged with completing an onerous task, there 
	is no way out of this assignment.
	\item[Status] (SD, 1-5):  A powerful kindred has punished you with Negative Patronage Status.  
	Each point of this Flaw represents up to three Status your detractor has, and requires an 
	appropriate back-story approved by the Storytellers.
	\item[Stench] (Nosferatu 72, 1):  Lose all ties on Stealth challenges automatically owing to 
	your offensive odor.  This includes uses of Obfuscate.
	\item[Traitor] (Nosferatu 74, 2):  You continually provide information about the secrets and 
	plans of your allies to a third party.  Every session you must provide the Storytellers with 
	what information you are revealing or your own secrets may start getting out.
	\item[Ward] (SD, 2-4):  You are devoted to the protection of a particular mortal 
	who for some reason is special to you, and who should never learn you are a vampire.  They are 
	however often getting into trouble or otherwise drawing unwanted attention.  Seeing them in 
	danger, or knowing they are in trouble and being unable to aid them, forces a 
	Self-Control/Instinct test versus four traits.  The more points this Flaw is worth, the more 
	frequently and severely your ward will require help.
\end{description}

\subsection{Mental Merits}
\begin{description}
	\item[Calm Heart] (LotN 116, 3):  Your unflappable resolve grants you +1 to all 
	Courage and Self-Control/Instinct tests.  Brujah may not take this Merit.
	\item[Code of Honor] (LotN 116, 1):  Having worked out a specific set of morals and 
	ethics separate from your Morality path with the Storytellers, gain a retest in 
	Social or Mental challenges which may cause you to violate your code.
	\item[Coldly Logical] (CG 25, 1):  Almost robotic in temperament, gain +1 trait when 
	someone is attempting to sway you through a Social challenge.
	\item[Common Sense] (LotN 116, 1):  The Storytellers may urge you against taking 
	potentially disastrous actions.  This Merit is well-recommended for new players.
	\item[Compassionate] (Brujah 68, 4):  You may spend a second Willpower to gain an 
	additional retest on all Conscience tests.
	\item[Concentration] (LotN 116, 1):  You may ignore situational trait penalties from 
	physical or mental distractions when engaged in a task requiring focus.
	\item[Dragon's Temperament] (Tzimisce 69, 3):  At the start of each session you or the 
	Storytellers may switch your Nature.
	\item[Eidetic Memory] (LotN 116, 2):  You have nearly perfect recall and may remember 
	even minute details with a Static Mental test.
	\item[Gifted] (SD, 3):  \emph{Toreador only.}  Naturally gifted in a single 
	form of \emph{Crafts} or \emph{Expression}, projects based on your specified skill-set 
	may require half the normal amount of time to complete, at Storyteller discretion.
	\item[Greater Colors] (SD, 3):  \emph{Toreador only.}  Able to perceive a greater 
	degree of colors than normal kindred, your world is awash with amazing patterns.  You may ask 
	two questions with a single successful \emph{Aura Perception} but are more easily entranced 
	by objects---regular works of art or performances will subject you to your Clan disadvantage if 
	you fail a Simple Test.
	\item[Immaculate Aura] (Malkavian 64, 1):  Your aura never shows signs of active 
	Derangements.
	\item[Introspection] (Sabbat 73, 1):  Gain a +2 trait bonus on Subterfuge or Aura 
	Perception challenges against someone who shares your Nature or Demeanor.
	\item[Iron Will] (LotN 117, 4):  Gain +3 traits when defending against Dominate or 
	mind-altering magic.  Does not protect against Presence or other social powers.
	\item[Light Sleeper] (LotN 116, 2):  You suffer no trait penalties while active during daylight 
	hours, and have an easier time of rousing yourself during the day, represented by a -2 
	difficulty for the requisite test.  You may rise earlier and stay awake later than your Morality 
	rating would otherwise dictate.
	\item[Natural Linguist] (LotN 116, 2):  Gain 2 languages per dot of \emph{Linguistics}.
	\item[Pelagic Harmony] (Lasombra 64, 3):  Gain an extra temporary Willpower when in 
	sight of the sea.
	\item[Time Sense] (LotN 116, 1):  You always know the time down to the exact minute.
	\item[Weather Sense] (Lasombra 63, 1-3):  You may make a Static Mental test to predict 
	upcoming weather.  See the Clanbook for more details.
\end{description}

\subsection{Mental Flaws}
\begin{description}
	\item[Amnesia] (LotN 117, 2):  You do not remember anything about your mortal life or 
	accounting, the events of which are up to the Storytellers.
	\item[Compulsion] (SD, 1):  Spend a Willpower to avoid engaging in your compulsion for 
	a scene or hour.  Work out the specifics of your compulsive action with a Storyteller, 
	which should be role-played frequently.  For more serious compulsions or obsessions see 
	Chapter \ref{sec:derangements}.
	\item[Conspicuous Consumption] (LotN 118, 4):  Only gaining sustenance from the organ 
	meats of your victims, you must kill to feed.  You must take \emph{Eat Food} and cannot 
	have dots of the \emph{Herd} Background.
	\item[Deep Sleeper] (LotN 117, 1):  All tests to wake during the day are increased by 
	2, and you wake later and sleep earlier than your Morality rating would dictate.
	\item[Flashbacks] (Sabbat 73, 6):  Wracked with flashbacks from the many traumatic events 
	of your existence, your starting Willpower each gather is determined by a Simple test:  
	winning means you are full, a tie that you are at half, and failure that you only have 2.  
	These totals are your maximum before losses from previous activities are included.
	\item[Guilt-Wracked] (CG 25, 4):  You must pass a Courage check to feed or you cannot 
	bring yourself to do so.  You are likely to often be hungry or starving.
	\item[Hatred] (SD, 2):  When presented with the object of your hate pass a 
	Self-Control/Instinct test of 4 traits or fly into Frenzy.
	\item[Hemetic] (Anarch 114, 4):  Unable to stand the taste of blood, you must make a 
	Static Physical test versus 6 traits to keep down vitae after feeding.
	\item[Image Obsession] (SD, 2):  \emph{Lasombra only.}  Incapable of seeing your 
	own image, you constantly fret and primp, obsessed with your imagined appearance.
	\item[Inept] (SD, 4):  An exceptionally slow-learner, double all XP costs for 
	Abilities and you may never have any Ability higher than 2.
	\item[Lunacy] (LotN 117, 2):  Suffer a -1 penalty to Self-Control/Instinct challenges 
	during the waxing or waning moon, -2 during the full moon.
	\item[Nightmares] (LotN 117, 1):  Suffering from frequent nightmares, you have a -1 
	trait penalty to all challenges at Storyteller discretion, normally decided night-to-night.
	\item[Pelagic Compulsion] (Lasombra 64, 2):  Tied to the sea, suffer a cumulative -1 
	trait penalty to all challenges for each night you have been unable to visit the ocean.
	\item[Phobia] (LotN 117, 2):  When presented with the object or situation you fear pass 
	a Courage test against 4 traits or flee.
	\item[Poor Taste] (SD, 1):  \emph{Toreador only.}  You are a true poseur, completely unable
	to distinguish between great art and utter trash, and wholly incapable of creating any 
	yourself.  You may not possess any dots in the Abilities \emph{Expression}, \emph{Crafts}, or 
	\emph{Performance}.
	\item[Poseidon's Call] (Lasombra 64, 1):  In calm or clear weather suffer a -1 penalty to 
	all Self-Control/Instinct and Courage tests, but gain +1 in storms.
	\item[Prey Exclusion] (LotN 117, 1):  You refuse to feed on a particular class or type of 
	individual.  Fall into an immediate frenzy if you discover you have done so.
	\item[Selective Digestion] (SD, 2):  You can only feed one one particular class or type of 
	individual.  If you accidentally feed from another, you gain no sustenance and may have to 
	throw a Self-Control challenge at Storyteller discretion.
	\item[Short Fuse] (LotN 118, 2):  Your passions run high and as such you suffer a -1 
	trait penalty on all Self-Control/Instinct tests.
	\item[Shy] (LotN 117, 1):  When dealing with three or more people suffer -2 traits on 
	Social challenges.  If it is a group of ten or more the penalty increases to -3.
	\item[Soft-Hearted] (LotN 117, 1):  You are down one trait on all challenges for the rest 
	of the evening after witnessing violence or suffering, and are very unlikely to either encourage 
	or perform violence yourself.
	\item[Speech Impediment] (LotN 117, 2):  Your stutter or other impairment causes difficulty 
	in communication, reflected as a -2 trait penalty to verbal challenges, including Thaumaturgy.
	\item[Territorial] (LotN 118, 2):  Claiming an area as your own, you must test against frenzy 
	if you spy an unexpected visitor, at a difficulty of four traits.  You are unlikely to leave 
	your turf save in exceptional circumstances.
	\item[Thirst for Innocence] (CG 25, 2):  Innocence of any kind drives you to Frenzy; make a 
	Self-Control/Instinct (3) test when you encounter it, at Storyteller discretion.
	\item[Uncontrollable] (Brujah 69, 5):  The Beast is so strong within you, lose all ties when 
	resisting against Frenzy or R\"{o}tschreck.
	\item[Vengeful] (LotN 118, 2):  Filled with a vindictive and retributive attitude, you must 
	spend a Willpower to avoid enacting your vengeance against someone who has wronged you when 
	available.
	\item[Weak-Willed] (LotN 118, 3):  Your feeble will limits you to 3 permanent Willpower and 
	causes you to suffer a -2 penalty on all Mental and Social challenges.  Anyone attempting to 
	Dominate you gains a free retest.
\end{description}

\subsection{Supernatural Merits}
\begin{description}
	\item[Addictive Blood] (SD, 3):  \emph{Followers of Set only.}  Your blood is truly 
	addictive to any mortal or kindred who tastes it.  So long as they remain blood bound to you 
	they must either spend a Willpower or win a Static Willpower test versus 3x the level of the bond 
	the first time they see you each evening to avoid actively trying to get another ``fix.''  The 
	addiction should still be role-played even if suppressed.
	\item[Attuned Taste] (Tremere 66, 2):  You may determine a vampire's generation with a small 
	taste of their blood.  This Merit provides no protection against being Bound to another kindred.
	\item[Benevolent Blood] (Malkavian 64, 1):  Your ghouls and others drinking from you do not 
	automatically gain Derangements.
	\item[Berserker] (SD, 2):  You have the capacity to enter frenzy at will, without throwing a 
	challenge.  You gain all the usual benefits and drawbacks of being in frenzy and have no 
	unusual ability to calm down or resist unwilling frenzy.
	\item[Bright Aura] (CG 25, 1):  Your aura always reads as mortal for \emph{Aura Perception} and other 
	related powers.
	\item[Controllable Night Sight] (Lasombra 63, 2):  You may flip your perception of light and 
	darkness at will.
	\item[Cosanguineous Resistance] (Giovanni 77, 1):  You can never become blood bound to anyone 
	sharing your mortal lineage.
	\item[Disembodied Mentor] (Malkavian 65, 5):  Your Mentor is not a physical entity but rather 
	a voice inside your own head.  You may call on this unique Mentor twice per story, but they must 
	be represented by the \emph{Mentor} Background as usual.
	\item[Embraced without the Cup] (Tremere 67, 3):  Something went wrong during your embrace and 
	you are not bound to the Council of Seven as all other Tremere are.
	\item[False Reflection] (Nosferatu 71, 3):  You may spend a Mental trait when engaging in 
	\emph{Obfuscate} to have your illusion appear on either camera or audio recording, or both if 
	you spend two traits.
	\item[Faint Reflection] (SD, 2):  \emph{Lasombra only.}  Instead of having no reflection 
	at all, you appear ghostly and ephemeral in mirrors, nearly translucent.
	\item[Haven Affinity] (Tzimisce 69, 3):  Spend a Mental trait and win or tie a Simple test to
	gain a +1 bonus on all challenges while within your haven for the following scene or hour, or 
	learn its approximate direction and distance relative to your current position.
	\item[Healing Touch] (CG 25, 1):  Instead of only being able to heal the wounds caused by your 
	feeding with a lick, your mere touch offers the same restorative effect.
	\item[Inoffensive to Animals] (CG 26, 1):  Animals do not shy away from you as they do from all 
	other kindred.
	\item[Lucky] (LotN 120, 3):  Three times per story you may call for a ``Luck'' retest on Contested 
	or Static challenges (see Chapter~\ref{sec:challenges}).
	\item[Magic Resistance] (LotN 119, 2):  Naturally shielded from blood sorcery you gain a +2 
	trait bonus against all uses of \emph{Thaumaturgy} or \emph{Necromancy} against you, but may 
	never learn these Disciplines.
	\item[Medium] (LotN 120, 2):  You may sense the presence of and speak with ghosts.
	\item[Nine Lives] (LotN 120, 6):  When a challenge would directly result in the death of your 
	character you may make an additional retest to survive, nine times in all, even multiple times 
	within the same challenge.  This is the only Merit which may be used in conjunction with others 
	in a challenge and need not be declared before the challenge is thrown.
	\item[Occult Library] (SD, 2):  You have a massive, non-magical library filled with strange and 
	arcane texts that may aid in non-Thaumaturgical research into the occult.
	\item[Oracular Ability] (LotN 120, 3):  Once per game session you may throw a Simple Test.  If you 
	win or tie you gain a retest which can be used once during the next scene or hour.  You may also 
	receive plot-specific portents from time to time, at Storyteller discretion.
	\item[Personal Masquerade] (Anarch 114, 3):  As a Caitiff you have successfully infiltrated a 
	Clan which considers you one of their own.
	\item[Proxy Kissed] (Giovanni 77, 4 or 8):  Gain additional physical Disciplines and begin play 
	bound to another character.  See the Giovanni Clanbook for details.
	\item[Revenant Disciplines] (Tzimisce 69, 3):  Begin play with your ghoul family Disciplines as 
	your in-Clans instead.
	\item[Sleep Unseen] (Nosferatu 71, 2):  Spend an extra blood when falling asleep to automatically 
	use \emph{Unseen Presence} while you slumber.
	\item[Spirit Mentor] (LotN 120, 3):  A unique spiritual entity follows you around and sometimes offers 
	advice and company, and with great effort it can affect the physical world.  This being is not a Mentor 
	and cannot perform remote services for you.
	\item[Strength of Shadows] (SD, 4):  \emph{Lasombra only.}  So powerful is your connection 
	to the dark of night that the light of the sun cannot easily dismiss them.  Instead of being instantly 
	destroyed shadows created with Obtenebration persist for up to four hours.
	\item[Sympathetic Bond] (Malkavian 66, 5):  Those who blood bond you also become bound in return.  
	A true three-point bond will supersede any sympathetic bond.
	\item[True Faith] (LotN 120, 7):  You possess a burning and unshakable faith in the deity.  See 
	Laws of the Night and a Storyteller for specific benefits and drawbacks.
	\item[True Love] (LotN 120, 4):  Gain +2 traits when actively protecting your true love.
	\item[Unbondable] (LotN 120, 4):  You can never be blood bound to another kindred, though you may 
	bond others as normal.  May only be purchased at character creation.
\end{description}

\subsection{Supernatural Flaws}
\begin{description}
	\item[13$^{th}$ Generation] (SD, 2):  No additional penalty other than being 13th 
	generation.
	\item[Ancestral Soil Dependence] (Tzimisce 70, 2):  Double the penalty for not sleeping in native 
	soil.
	\item[Beacon of the Unholy] (CG 26, 2):  Suffer the effects of \emph{True Faith} when near any place 
	of worship as your evil and supernatural aura recoils in horror.  Hunters have an easier time 
	picking you out of a crowd.
	\item[Bound] (CG 26, 2):  Begin play three points bound to another character, normally an NPC. Work 
	out the details with the Storytellers.
	\item[Can't Cross Running Water] (LotN 121, 2):  Streams and rivulets at least 2' deep are impassible 
	unless you are inside a closed vehicle.
	\item[Cast No Reflection] (LotN 121, 1):  Your body does not appear in mirrors or other reflective 
	surfaces, which can be an obvious breach of the Masquerade.
	\item[Clan Weakness] (Anarch 114, 2):  As a Caitiff you suffer another Clan's weakness not already described 
	by other Flaws.  Available to Caitiff characters of any Sect.
	\item[Cold Breeze] (CG 26, 1):  Suffer a -1 penalty on all Social tests with mortals as a chill wind 
	follows you everywhere.
	\item[Cursed] (LotN 120, 1-5):  Unique and custom problems follow you everywhere.  Work with a 
	Storyteller to define the limits and effects of your curse.
	\item[Dark Fate] (LotN 121, 5):  All of your plans will fall to ruin and you will be slain or otherwise 
	removed from play at a time and manner of the Storytellers' choosing with no chance to escape it.
	\item[Death's Reflection] (Lasombra 65, 3):  Instead of the usual Clan disadvantage your reflection 
	presents your true age, a dessicated and decayed corpse.
	\item[Deathsight] (CG 26, 2):  Gain the traits \emph{Callous} and \emph{Oblivious} as you see no 
	beauty in the world around you; everything appears to be in a constant state of disrepair and 
	decrepidation.
	\item[Decrepitude] (Anarch 114, 3):  Your weakened body does not heal normally; when suffering 
	aggravated wounds win or tie a Simple test to avoid gaining permanent \emph{Repugnant} traits, limit 
	of five.
	\item[Eerie Presence] (LotN 121, 2):  Your disquieting presence causes you to be -2 traits on all 
	non-intimidating Social challenges with mortals.
	\item[Enemy of Shadows] (SD, 4):  \emph{Lasombra only.}  Not only are you not immune to your own 
	\emph{Shroud of Night}, any \emph{Arms of the Abyss} you create (including those through 
	\emph{Black Metamorphosis}) may attack you instead of your intended target.  Win or tie a Simple 
	test each time you create tentacles or else they consider you their primary foe.
	\item[Grip of the Damned] (LotN 121, 4):  Instead of causing the Kiss when feeding, your bite 
	causes nothing but terror and pain, making feeding or establishing herds difficult.
	\item[Haunted] (LotN 121, 3):  A malicious wraith haunts you forever, causing mischief and problems 
	in your night to night existence.
	\item[Heartless] (SD, 4):  Someone has used the advanced level of Serpentis on you, granting 
	you all the benefits and drawbacks of that Discipline, but you do not have possession of your own heart.  
	If another kindred has it, likely an Elder Follower of Set, you must obey them or risk destruction.  If 
	it is simply missing, the stress of not knowing may result in penalties similar to the \emph{Nightmares} 
	Flaw.
	\item[Infectious] (Malkavian 66, 3):  Those you feed upon gain one Derangement for every three 
	Blood traits you take, which fades in one week.
	\item[Light-Sensitive] (LotN 122, 5):  Sunlight causes double damage and even the light of the full 
	moon causes one lethal wound per turn.
	\item[Lord of the Flies] (CG 26, 2):  The constant presence and buzzing of flies causes you to suffer 
	a -1 penalty on all Social or \emph{Stealth}-related challenges, including \emph{Obfuscate}.
	\item[Magic Susceptibility] (SD, 2):  Naturally weak against blood sorcery you suffer a -2 
	trait penalty against all uses of \emph{Thaumaturgy} or \emph{Necromancy} against you.
	\item[Nosferatu Caitiff] (SD, 2):  Embraced as a Nosferatu, the blood didn't fully take hold and you have 
	been ousted as a Caitiff.  You may not begin play with any Appearance-based Social traits and each one costs 
	4xp to purchase.
	\item[Ravaging Years] (Anarch 114, 2):  Your body is not truly immortal and ages one year for every 
	25 you exist.  Aggravated wounds also speed this process, one year per wound.
	\item[Repelled by Crosses] (LotN 121, 3):  Spend a Willpower to remain in an area where a cross is 
	visible for the next scene or hour.  Touching or being touched by a holy symbol causes aggravated wounds.
	\item[Repelled by Garlic] (LotN 121, 1):  Spend a Willpower to remain within 10' of garlic for the next 
	scene or hour.  If a clove of garlic is ever forced into your mouth, suffer an aggravated wound.
	\item[Scales] (SD, 1-3):  \emph{Followers of Set only.}  During your embrace the blood of 
	Set twisted your body, hardening patches of it into scales.  Gain the Negative Trait \emph{Bestial} 
	once for each point of this Flaw.
	\item[Shadow Walker] (Giovanni 78, 6):  You travel the Shadowlands as you move through the physical 
	world, subject to all of the creatures and obstacles therein.
	\item[Stigmata] (Malkavian 66, 2-4):  Seep blood through open wounds and gain various penalties 
	depending on the severity of this Flaw.  See the Malkavian Clanbook for specific details.
	\item[Superstition] (Anarch 115, 1-5):  You believe in and are affected by popular vampire 
	stereotypes which worsen with more points in this Flaw.
	\item[Taint of Corruption] (SD, 1):  Plants wither at your approach and will die if you 
	touch them.  Gardens are all but off-limits to you.
	\item[Thaumaturgically Inept] (Tremere 67, 5):  All blood magic casting times are increased by 
	five minutes, all related tests are at +1 difficulty, and you suffer a -1 trait penalty for all 
	Social tests against higher-ranking Tremere.
	\item[Touch of Frost] (LotN 121, 1):  Your skin is ice-cold, making physical contact with you 
	uncomfortable for mortals.  Suffer a -1 Social trait penalty against any mortal who has touched or 
	been touched by you.
	\item[Uncontrollable Night Sight] (Lasombra 64, 2):  Your perception of light and darkness 
	switch randomly.  At the start of every scene throw a Simple test; a loss results in light and 
	darkness inverting unfavorably for the scene.
\end{description}