\section{Experience}
\label{sec:xp}
As characters progress through this collaborative story they grow and change, 
this process represented by experience points, also called XP.  Experience can 
be spent to purchase new Abilities, Disciplines, Traits, and all number of other 
aspects on the character sheet.  However, the more a character learns, the harder 
it is to learn more; as a character progresses through the months and years of 
\emph{Sanguine Dreams} the rate at which they earn XP slows to make sure newer 
characters always have a chance to close the gap---this includes XP earned but not 
yet spent.  Experience is earned by playing your regular PC; portraying NPCs does not 
add to your XP total, and XP is not transferable between characters.

\subsection{Earning XP}
\begin{itemize}
	\item Earn 1 XP per game session where you spent a majority of the time in character
	\item Gain 1 bonus XP if you play at every game in a month
	\item Gain 1 bonus XP if you bring a new player to game
	\item Additional bonuses may be awarded by the Storytellers for outstanding 
	costuming or role-play, mentoring new players, donating props, and/or 
	generally improving the game experience for everyone
\end{itemize}

\begin{center}
\begin{tabular}{ | c | c | }
	\hline
	\textbf{Total XP Earned} & \textbf{Monthly XP Cap} \\
	\hline
	0 - 59 & 6 XP \\
	60 - 109 & 5 XP \\
	110 - 149 & 4 XP \\
	150 - 179 & 3 XP \\
	180 - 199 & 2 XP \\
	200+ & 1 XP \\
	\hline
\end{tabular}
\end{center}

\subsection{Spending XP}
\begin{itemize}
	\item You may spend XP at any time by turning in a spend sheet, available at game, or by 
	messaging the proper Storyteller on the website.  Purchases take effect the game following their being 
	logged by the Storytellers, typically after one full week.
	\item Individual Abilities, Backgrounds, Disciplines, Virtues, and Willpower may only be 
	increased by one dot each per week.
	\item Influences may only be purchased at level 1 with XP, future growth must be done through 
	the Influences rules.  See the \emph{Mortal Manipulations} packet for more information.
	\item Learning an out-of-Clan Discipline requires a teacher who possesses more dots 
	in the Discipline than that which you are learning to sign off that they are teaching you.
	\item A Clan-specific out-of-Clan Discipline requires not only a teacher as above but also 
	the consumption of a trait of Blood from that Clan per level at the time of purchase.
	\item Out-of-Clan Combo Powers are not permitted.
	\item Backgrounds may not be purchased without running relevant downtime scenes with a Storyteller.
	\item Only one Ability may be raised to 5 per character.
	\item Purchases lost during play still count against your earned XP total without refund.
	\item Note that not all Merits can be purchased after character creation, nor all Flaws or Negative Traits bought off.
\end{itemize}

\begin{center}
{\footnotesize
	\begin{tabular}{| l | c || l | c |}
	   \hline
	   \textbf{Item} & \textbf{XP} & \textbf{Item} & \textbf{XP} \\
	   \hline
	   Physical Trait &  & Virtue Trait & 3 \\
	   Social Trait & 2 & Morality Trait & 2 \\
	   Mental Trait & & Willpower Trait & 3 \\
	   \hline
	   Ability & 1 & Removing a Neg. Trait & 2 \\
	   Ability Specialization & 2 & Removing a Flaw & 2x Traits \\
	   Background Trait & 1 & Buying a Merit & 2x Traits \\
	   \hline
	   `In Clan' Discipline & 3, 6, 9$^{\dagger}$ & `Out of Clan' Discipline & 4, 7, 10$^{\dagger}$ \\
	   \hline
	\end{tabular} \\
   {\footnotesize $^{\dagger}$ Cost for Basic, Intermediate, and Advanced levels, respectively}
}
\end{center}
