\section{Introduction}
\subsection{The Game within the Game}
\emph{Vampire: the Masquerade} is a game which operates on many levels---political intrigue, 
explosive violence, and begrudging alliances---all of which combine to create a rich tapestry 
for our setting.  Beneath the surface however there is another game, that subtle and pervasive 
tug-of-war for the hearts and minds of the mortal population.  Called ``Influences,'' this 
document contains everything you need to know in order to dive into this cat-and-mouse contest 
that can have tangible repercussions in our regular Sunday nights.

A special type of Background, \emph{Influences} represent different spheres of mortal society 
in which your character may have sway.  With Influences your character can accomplish many 
endeavors subtly and without personal risk.  While the process of using Influences is slow 
compared to running a scene with a Storyteller, it can simplify a great many actions and 
accomplish more long-ranging tasks that are best left to mortals, such as faking legal documentation, 
building hype about an upcoming club event, or acquiring weapons.

Unlike \emph{Allies} or \emph{Retainers}, dots in the Influence Background are not representative 
of individual or specific people your character controls; rather it is a metric to show just how 
much pull or sway they have over that specific mortal arena.  With just one dot your character may 
have the ability to gain advanced warning or knowledge of upcoming events, while with five dots 
your character may be able to change whole Domain landscapes, be they economical, political, or literal.

Each specific Influence is rated from one to five, which represents increasing control over an aspect 
of mortal society.  Every Influence cycle, usually a two-week period, players submit their 
desired actions, examples of which are detailed later in this document, and wait to hear 
whether or not they were ultimately successful.  Standing in the way of success are other 
Domain denizens, who may have a personal grudge against their enemies, or are acting at cross-purposes 
to a large swath of kindred.  A full description of each available sphere of influence can be found 
in the next section.

If your actions are not successful and you want to determine why, or you have an interest in 
tracking down just who pulled specific strings, there are mechanics to do just that, all detailed 
in the next section, with specific examples of Influences in play in the final chapter.

Starting to use Influences can be an intimidating process to new players, but it is the Storytellers' 
goal to make them approachable, interesting, and a compelling source of story.  When in doubt, please talk 
them and ask your questions!

\subsection[Influence Spheres]{The Spheres of Influences}
Influence is broken into 15 different areas or ``spheres'' a vampire may control.  While many 
can provide similar results, each has a distinct and valuable use within the World of Darkness.  
Those who possess much Influence are well-advised to keep others from becoming their rivals, while 
those without are encouraged to tear down the figures standing in their way. \medskip

\begin{description}
	\item[Bureaucracy] -- controlling government agencies and paperwork
	\item[Church] -- worship sites and sects of major religions
	\item[Finance] -- the world of business and accounting
	\item[Health] -- from hospitals to clinics and healthcare workers of every stripe
	\item[High Society] -- the world of the posh and the popular
	\item[Industry] -- the means of production are at your disposal
	\item[Legal] -- protecting or condemning the innocent and the corrupt alike
	\item[Media] -- when you're in charge, all news is good news
	\item[Occult] -- small or undervalued belief systems and the people who follow them
	\item[Police] -- wielding not just a badge, but the entire force
	\item[Political] -- he who controls the government sets the rules
	\item[Street] -- homeless, hookers, and minor street gangs
	\item[Transportation] -- getting goods in and out
	\item[Underworld] -- organized or at least structured crime
	\item[University] -- higher education and on-campus resources
\end{description}
	
\subsection{Quick Rules}
\begin{itemize}
	\item Influence cycles last two weeks, lasting from one submission due date until the next
	\item No character may have more dots of Influence than they have traits (the total of 
	Physical, Social, and Mental)
	\item Some levels of Influences may be limited by the environment; Sonoma County may not 
	have enough Industry for multiple characters to have level 5, for example
	\item Influence actions do not resolve immediately; success and failure will be reported 
	at the designated game sessions
	\item Idle influence fades over time; control must be maintained or it will eventually 
	be lost, at a rate determined by the Storytellers
	\item Influences cannot be grown through spending XP, it must be done through the use of 
	the \emph{Growth} action
	\item No Influence can affect areas outside of Sonoma County without use of the \emph{Fame} 
	Background, which represents increased geographical pull in a particular sphere
\end{itemize}