\section{Introduction}
\label{sec:introduction}
In this supplemental rule guide for \emph{Sanguine Dreams}, the strange and wondrous Disciplines 
of Thaumaturgy and Necromancy are explored, along with the Clans who can wield 
those amazing powers.  These specific Disciplines have significant advantages over those which 
come naturally to other Clans, but also significant drawbacks both in the raw costs to cast 
the spells and the secrecy to which their practitioners must keep.

\textbf{This guide is not designed to be read by every player} -- the contents here are some of 
the most secret and carefully-guarded in all of kindred society, and are far from general knowledge.  
The Clans which wield these powers often have complex and complicated internal structures, invisible 
to those outside, and the Storytellers highly recommend players not actively role-playing 
characters in those Clans to skip this guide entirely.

Thaumaturgy and Necromancy differ from other Disciplines by encompassing a wide range of powers, 
divided into paths, as well as complicated rituals which can provide longer-lasting effects than 
most any other power in the game.  Practitioners of these dark arts are loath to divulge their 
secrets, even descriptions of what is or isn't possible, and those who talk too freely are often 
``called away'' unexpectedly, not to be seen by local kindred again.

This guide should be considered the authoritative source of all rules related to the use of these 
two Disciplines, though it makes frequent reference to other source material previously published 
by White Wolf, the original creators of \emph{Vampire: the Masquerade}.  If ever there is a 
conflict between the original books and this volume, the rules presented here and in other guides 
created for \emph{Sanguine Dreams} take presidence.

The powers of Thaumaturgy and Necromancy are wide and varied, and the Storytellers encourage 
players to remember the Golden Rules, to expand upon and elaborate on the thematic elements which 
make these Disciplines so interesting.  When in doubt, please see a Storyteller.

The contents of many sourcebooks went into the construction of this document, and where available 
each power's source has been included in its writeup.  Often the original source provides additional 
thematic elements or role-play opportunities with these powers, but the final mechanics that will 
be used in \emph{Sanguine Dreams} are all presented in this volume, disregarding the original 
writeups.  As a unilateral rule powers not appearing in this volume are not approved for play. \\

\begin{minipage}{0.5\textwidth}
   \begin{flushleft}
	{\scriptsize
	\emph{SD} --- Sanguine Dreams-specific \\
	\emph{LotN} --- Laws of the Night \\
	\emph{Grey} --- Laws of the Night (2\textsuperscript{nd} Ed) \\
	\emph{ST} --- Storyteller's Guide \\
	\emph{BM} --- Blood Magic (2\textsuperscript{nd} Edition) \\
	\emph{Elysium} --- Laws of Elysium (2\textsuperscript{nd} Ed) \\ }
	\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
   \begin{flushleft}
	{\scriptsize 
	\emph{Clan} --- Clanbook \emph{(Clan)} \\
	\emph{Night} --- The Long Night (Dark Ages) \\
	\emph{Anarch} --- Guide to the Anarchs \\
	\emph{NYBN} --- New York by Night (2\textsuperscript{nd} Ed) \\
	\emph{CamTT} --- Guide to the Camarilla (Table-Top) \\
	\emph{BS} --- Blood Sacrifice (2\textsuperscript{nd} Ed) \\ }
	\end{flushleft}
\end{minipage}