\subsection{Thaumaturgical Rituals}
\label{sec:trituals}

\emph{((General text about what rituals are and how they differ from paths here))}

\subsubsection{General Rules}
\begin{itemize}
	\item Learning a new ritual requires explicit Storyteller permission and role-play 
	justification for your character having learned it.
	\item All ritual effects cease at dawn unless otherwise specified, or upon the death of 
	all contributors to its casting.
	\item Rituals are listed with the Tremere Rank required to petition for its study.  Those 
	marked ``Any'' are available to all Tremere.  For other Clans, see availability writeups 
	in Section~\ref{sec:clans}.
	\item Most rituals do not cost Blood to cast, but do take a length of time specified either 
	by their level or individual description.
	\item All rituals require material components, many of which will be destroyed in the 
	casting.  The acquisition of these sometimes rare materials is an important aspect to 
	playing a Thaumaturge, and some may be very difficult to obtain.  Scenes to acquire 
	these resources should be run with the Storytellers.
	\item Rarely is a ritual's success or failure evident at the time of casting.
	\item Any items or locations enchanted with rituals must be represented by Storyteller-signed 
	item cards.
	\item Bonus traits and retests gained through rituals do not stack with those from Merits or 
	Ability Specializations, and must be similarly declared before a challenge is thrown.
	\item Rituals specifically noted as ``non-Camarilla'' or with a Clan name are only available 
	to characters that meet those requirements.
	\item Some rituals permanently reduce a character's available blood pool until ended.  Any 
	such reductions should be represented by an ``X'' through the character's final available blood 
	pool dot.  These powers lower a character's ability to store blood and as such the missing point 
	can not be filled.
	\item Some rituals can be ended at the will of the caster.  If in combat, the power ceases at the 
	end of the current combat turn.
	\item Each caster receives a free ritual when they increase their knowledge of their primary 
	Thaumaturgical path. This ritual can be at or below the new dot's level (Basic, Intermediate, Advanced).
\end{itemize}

\subsubsection{Basic Rituals}
All Basic rituals have a static difficulty of 5 traits and a casting time of 10 minutes unless otherwise stated.  
A character wishing to learn a Basic ritual must first have at least one dot of \emph{Thaumaturgy}. \\

\begin{description}
	\item[Bind the Accusing Tongue] \emph{(CamTT 109, A5)} \hfill \\ 
	This power lays a compulsion upon the target that prevents them from speaking ill of the caster, no matter the 
	consequences or circumstances.  Requiring an effigy of the target made with a lock of their hair and a black 
	silken cord, if successful this ritual requires the subject to beat the thaumaturge in a Contested Mental 
	challenge (both sides may retest with Willpower only) in order to speak ill of them for the remainder of the 
	scene.  The caster must have the effigy on their person and if the black cord is untied the ritual ends. \\

	\item[Blood Into Water] \emph{(NYBN 48, Any)} \hfill \\
	This simple ritual, requiring a small basin of clean water and one trait of the caster's blood to be dripped 
	into it during the casting, turns all spilled blood in the immediate area to water.  This power is often used 
	to preserve the Masquerade or otherwise clean up after particularly violent events. \\

	\item[Blood Mead] \emph{(ST 64, A3)} \hfill \\ 
	Created by Tremere who study the \emph{Vine of Dionysus} path, this ritual requires a special concoction of 
	mead (fermented honey) and two traits of the caster's Blood.  By drinking the potion immediately after 
	casting, they gain an additional Healthy health level but suffer a one-trait penalty on all Dexterity- or 
	Intelligence-based challenges as determined by the Storyteller, for the rest of the evening. \\

	\item[Blood Mastery] \emph{(Tremere 56, Any)} \hfill \\
	By mixing a trait of your own vitae with a like amount from a subject, then slowly burning the mixture over 
	open flame, you gain limited power over them.  The next challenge you engage in against the subject automatically 
	succeeds (though a staking challenge still requires the two Simple tests to be thrown). Relenting to a challenge 
	does not trigger this ritual's effects. \\

	\item[Blood Rush] \emph{(Grey, non-Camarilla)} \hfill \\
	This ritual prevents the thaumaturge from feeling the effects of a low blood pool. By chanting and turning in slow 
	counterclockwise circles, the caster may for the rest of the night spend a Physical Trait in order to negate any 
	penalties for having a low blood pool, such as risk of hunger frenzy or effective Virtue levels. Each such 
	expenditure negates penalties for one scene or hour. \\

	\item[Blood Walk] \emph{(Elysium 80, A4)} \hfill \\
	This ritual allows you to trace the lineage of a kindred subject, requiring either their presence in the same room 
	for the duration of the ritual or a trait of their blood.  With a successful challenge you learn the identity of the 
	subject's sire, generally at least enough to use the Politics Ability on.  By spending an additional 10 minutes and 
	with another successful Mental challenge you may learn their grandsire's identity if the first challenge was 
	successful.  This process may be repeated one additional time to learn the subject's grand-grandsire. \\

	\item[Brand of the Paramour] \emph{(ST 65, Any)} \hfill \\
	By obtaining a single Blood trait from mortal twins, two traits in total, enchanting them with words of power, 
	and having both the caster and a ghoul equally imbibe the mixture, should the ghoul in future be injured, the 
	kindred will feel a ghost pain in the same location, though this power cannot be used to ascertain the amount 
	of damage received. The thaumaturge receives no wounds or mechanical penalties for this ghost pain, even if the 
	ghoul is slain. This ritual lasts until the ghoul is Embraced, killed, or reverts to mortality due to lack of 
	vitae. \\

	\item[Bureaucratic Condemnation] \emph{(BM 91, A5)} \hfill \\
	The hostile version of \emph{Deny the Intruder}, by sending an effigy of the target made with their hair and a 
	trait of their blood through the postal system, all Endeavors they attempt during the next Influence Cycle are 
	delayed or thwarted due to complications. \\

	\item[Burning Blade] \emph{(CamTT 110, A5)} \hfill \\
	By suffering an unsoakable Lethal wound and pouring three blood traits onto a bladed weapon, a thaumaturge can cause 
	the weapon to become wreathed in green fire when drawn. If the weapon is used in a successful attack, one inflicted 
	wound is upgraded to Aggravated, for the first three such hits. It is impossible to pull one's punch while wielding 
	such a weapon; the additional damage is always dealt. This power is an obvious breach of the Masquerade. The flames 
	automatically activate the first time the weapon is drawn after the ritual is cast, and its effects last until three 
	successful strikes are made, it is sheathed, or at sunrise. \\

	\item[Calling the Restless Spirit] \emph{(Elysium 80, A3)} \hfill \\
	A single spirit may be summoned and communicated with by spending ten minutes with the ghost's dead body or in an 
	area it frequently haunts, accompanied with the burning of incense native to their homeland.  If successful, the 
	spends another five minutes in intense concentration to facilitate the communication; any interruptions or actions 
	ends the ritual immediately.  This power gives the thaumaturge no special ability to see, command, or control the 
	spirit, but does permit two-way communication.  This power will work on a vampire who has died the Final Death, but 
	not through diablerie. \\

	\item[Communicate with Kindred Sire] \emph{(LotN 185, Any)} \hfill \\
	Meditate on an item once belonging to your sire for a full half hour. Afterward you establish a telepathic link 
	with them for 10 minutes, regardless of their location. The sire must be awake for this ritual to succeed. \\

	\item[Craft Bloodstone] \emph{(ST 68, A4)} \hfill \\
	By soaking a simple pebble in three traits of the caster's vitae over the course of three consecutive nights, 
	requiring several minutes of incantations each night, the caster becomes linked to the stone and may thereafter 
	determine its general direction and distance, regardless of how far away the stone is. Casting this ritual costs 
	a permanent Blood trait which cannot be recovered until either the stone is destroyed or the ritual unwoven. A 
	stone so enchanted must be represented by an item card, and is permanent. \\

	\item[Crimson Sentinel] \emph{(Night 128, A4)} \hfill \\
	By inscribing arcane runes on the interior of a small room's entrances with one trait of a subject's blood and 
	ivy ash, they will be barred entry unless they win a Static Physical challenge of 8 traits, retested with Willpower.  
	This power lasts until sunrise or until the obvious markings are disturbed.  Larger rooms require increased casting 
	time and blood investment, and this power does not prevent an individual from leaving the room once inside. \\

	\item[Dedicate the Chantry] \emph{(Tremere 57, A7)} \hfill \\
	This ritual reinforces Clan Tremere's connection to a particular building, dedicating it as a Chantry, and requires 
	the caster to circle the grounds, sprinkling stagnant water in a process that takes at least one hour. All 
	Thaumaturgical rituals cast while inside a Chantry gain a +1 Trait bonus for the purpose of ties. Other thematic 
	and mechanical effects are at Storyteller discretion.  Effects last for one year.\\

	\item[Defense of the Sacred Haven] \emph{(LotN 185, Any)} \hfill \\
	Spend a Blood trait as you paint protective sigils across the doors and windows of a room in a process taking one 
	hour.  So long as you remain within the room, sunlight is mystically prevented from entering the room, to a 
	maximum of one story. \\

	\item[Deflection of the Wooden Doom] \emph{(LotN 185, A4)} \hfill \\
	Sit inside a circle of wood for a full hour to cast this ritual.  Keep a splinter of wood beneath your tongue.  As 
	long as the splinter remains there, or until the next dawn, whichever is sooner, you are protected by this ritual.  
	The first stake to successfully impale your heart (indicated by both Simple Tests succeeding) mystically crumbles 
	to dust, which ends the protection. \\
	
	\item[Deny the Intruder] \emph{(Tremere 58, A6)} \hfill \\
	A ritual designed to help protect important Tremere holdings, this power, enacted by writing the required occult 
	glyphs in charcoal on a piece of paper and sending it through the postal system, hides the designated building 
	from outside Influence for one year; all Influence Endeavors aimed at the building, whether helpful or harmful, 
	require more actions than normal to have a chance of succeeding. \\
	
	\item[Devil's Touch] \emph{(LotN 185, Any)} \hfill \\
	This ritual enchants one penny which, when placed on a mortal's person, grants them the negative Traits 
	\emph{Repugnant} and \emph{Obnoxious} until dawn. \\
	
	\item[Donning the Mask of Shadows] \emph{(Elysium 80, A5)} \hfill \\
	By tying a thin black linen blindfold across the eyes a thaumaturge may emulate the Obfuscate power of 
	\emph{Unseen Presence} for one use.  Before starting the ritual the caster must decide how many Mental traits they 
	are sacrificing, minimum of one.  For each Mental trait so invested the power lasts an additional hour, or until 
	the faux-Obfuscate is broken by another means. \\
	
	\item[Encrypt Missive] \emph{(ST 65, A3)} \hfill \\
	Centuries of secrets have been safely communicated through this ritual, requiring a message to be written in the 
	caster's own blood, one trait at minimum.  The caster names one individual for whom the message is intended; if 
	successful all others will interpret the words as meaningless scribbles, its true substance only visible to the 
	caster and the target.  The letter smudges beyond recognition at the end of one story. \\
	
	\item[Engaging the Vessel of Transference] \emph{(Night 128, A5)} \hfill \\
	By preparing a clay pot or urn with specific mystical carvings, any blood placed inside, limit of one trait, will 
	be instantly exchanged with one trait of the next non-caster who touches it, causing them to involuntarily shiver.  
	A Static Mental challenge, retested with \emph{Occult} could determine that something magical happened, but 
	otherwise there is no sign that anything untoward has transpired. This power is sometimes used to stealthily blood 
	bond others, poison them, or otherwise obtain their blood. An empty jar will remain viable for one story but a full 
	jar expires at dawn, reducing all contents to ash. \\
	
	\item[Enhancing the Curse] \emph{(ST 65, A4)} \hfill \\
	Used almost exclusively to punish misbehaving ghouls, this power bestows a terrible vulnerability to sunlight on the 
	subject for as long as the victim has vampiric vitae in their system, to a limit of one story.  Enacting this ritual 
	requires the caster to strike or scratch the ghoul, causing at least one wound of injury. \\
	
	\item[Escape to a True Friend] \emph{(CamTT 114, A4)} \hfill \\
	One of the only true teleportation powers available to kindred, this ritual requires the thaumaturge to spend six 
	hours a night casting on six successive nights, each night requiring two blood points to be used in the enchanting.  
	Through this process a two-meter circle is inscribed on the floor, which afterward cannot be disrupted by normal 
	means.  By stepping into the circle and speaking the True Name of a friend, the thaumaturge and up to one other person 
	will be teleported instantly to a safe area near the named friend.  This power requires the permanent investiture of a 
	Blood point as the ritual circle is permanent until unwoven or wholly destroyed. \\
	
	\item[Extinguish] \emph{(ST 64, A3)} \hfill \\
	By first casting the ritual and then pinching out a candle flame (a 1 trait Courage check) and spitting on the floor, 
	the caster of this ritual gains power over natural fire. For the rest of the night, by speaking a mystical command word 
	a single flame up to the size of a small bonfire can be completely extinguished, which ends the ritual. \\
	
	\item[Illuminate Trail of Prey] \emph{(???, Any)} \hfill \\
	By burning a length of white satin ribbon that has been in the caster's possession for at least the twenty-four hours 
	prior to casting the ritual and naming a person with whom the thaumaturge is familiar that person's tracks are made 
	visible to the caster, who has a rough idea of how long ago they have been made that evening.  These tracks cease 
	where the target crosses water or reaches their destination, as determined by the Storytellers, but will allow the 
	target to be followed whether they were on foot, driving, or even have taken to the air. \\
	
	\item[Impassable Trail] \emph{(ST 66, Any)} \hfill \\
	By preparing an owl's feather steeped in kindred vitae or the burned ashes of toad legs and keeping the material with 
	them, the caster can pass through even the densest woods or other terrain without leaving so much as a trace of their 
	passage, unless someone looks with a power such as \emph{Heightened Senses}. \\
	
	\item[Impressive Visage] \emph{(ST 66, A3)} \hfill \\
	By placing a sprig of dried mint and two eyelashes from an ugly child in their left shoe as they cast this ritual the 
	Tremere gains a great deal of personal affability and charisma, gaining a +2 trait bonus for the comparison of ties 
	on in-person Social challenges for the rest of the evening. \\
	
	\item[The Imp's Affliction] \emph{(ST 66, Any)} \hfill \\
	By writing a mortal subject's name on a piece of paper and burning it, they contract a short-lived, uncomfortable, and 
	embarrassing illness where their nose runs uncontrollably, their throat becomes raw and raspy, and their eyes constantly 
	brim with mucus tears.  This power lasts for one scene and specific mechanical effects are up to the Storytellers. The 
	vampire must be familiar with the subject, at least having engaged them in conversation, or possess a strong sympathetic 
	link to the person, such as blood or a favored object. \\
	
	\item[Incantation of the Shepherd] \emph{(Cam 110, Any)} \hfill \\
	By holding two glass prisms up to the eyes and rotating in a slow circle for the totality of the casting time, the 
	thaumaturge either learns the direction and distance of every member of their herd, or the closest three mortals from 
	whom the caster has fed before if they possess no herd.  This ritual has a maximum range of five miles times dots in the 
	\emph{Herd} Background, minimum one. \\

	\item[Jinx] \emph{(ST 66, A3)} \hfill \\
	By sacrificing at least one trait of the victim's blood, the caster inflicts another kindred with terrible luck.  For one 
	scene anything that can go wrong does -- their shoelaces become untied causing them to trip, their car fails to start, they 
	miss their bus.  This ritual won't do any direct damage to the target and any specific combat-related effects are up to the 
	Storyteller on scene. \\
	
	\item[Learning the Mind Enslumbered] \emph{(ST 67, A4)} \hfill \\
	By placing a small penny or coin on a torpid or deceased kindred's eye, or close approximation thereto in the case of truly 
	decomposed individuals, the caster will hear the body's spirit tell the particulars of how it came to be in its current 
	state, though the conversation is one-sided and the spirit cannot be asked for more detail.  This ritual takes thirty minutes 
	to cast and only works on the undead. \\

	\item[Luminous Vitae] \emph{(NYBN 48, Any)} \hfill \\
	A precursor to modern-day forensic analysis, this ritual, requiring two fresh owl feathers, allows the caster to observe even 
	the most minute trace of blood in a room by a tell-tale purple glow. While not effective on blood contained inside containers, 
	including bodies, through this ritual a thaumaturge can be sure they have cleaned all traces of blood from an area. \\
	
	\item[Mourning Life Curse] \emph{(ST 67, A5)} \hfill \\
	Drinking a dram of thrice-distilled crocodile blood then making a paste of copal oil, ground eyebright, and dates, the caster 
	prepares a sticky goo that, when placed on the eyelids of a mortal, will cause them to weep blood tears after hearing the 
	two-line command incantation.  This bleeding is uncontrollable and painless but slow, with one full point draining every five 
	minutes.  This loss continues until the thaumaturge stops concentrating on the subject; if the caster takes any actions other 
	than simple movement while concentrating, the ritual ceases.  Some Tremere use this power to feed on sleeping mortals. \\
	
	\item[The Open Passage] \emph{(LotN 185, A4)} \hfill \\
	By spreading your blood in intricate patterns across a door, wall, or window, you allow it to become insubstantial for a 
	short time.  Creating a passage wide or tall enough for one person to pass costs one blood and takes 20 minutes to cast, two 
	people two blood and 40 minutes, and three people three blood and 60 minutes.  In all cases the opening only lasts three 
	combat turns (roughly ten seconds) and the Storyteller is the final arbiter of how many people can pass 
	through safely. \\
	
	\item[Power of the Invisible Flame] \emph{(???, A5)} \hfill \\
	By spending twenty minutes in contemplation near a fire of at least torch size and drinking a potion made of chameleon scales 
	and one trait of vitae, as well as suffering one Aggravated wound, any fire the caster creates through the path 
	\emph{Lure of Flames} are invisible for the rest of the night, though they are no less effective.  This power only affects 
	flame directly created through that path; if other materials catch fire the flames are visible as normal. \\
	
	\item[Principal Focus of Vitae Infusion] \emph{(LotN 186, A5)} \hfill \\
	Casting this ritual, which requires trait of your blood which becomes infused into a hand-held item serving as the material 
	component of this spell, allows you to store blood for future use.  At any point within the same story you may issue the 
	command word, which causes the blood to seep back out of the item.  If another is present at the time of casting you may 
	have the object react to their command as well, though as the blood is still your own.  Any items infused with this ritual 
	must be represented with a signed item card, and only one object can be reverted per action. \\

	\item[Purge the Inner Demon] \emph{(ST 67, A4)} \hfill \\
	Through the use of this power a kindred can be made resistant to the ravages of the Beast.  By pushing a sturdy pin through 
	their own hand, the caster separates another's beast from their psyche, granting them immunity to all frenzy checks not 
	caused by a supernatural source (such as \emph{Drawing out the Beast} or \emph{Voice of Madness}) for a number of hours equal 
	to half of the caster's Morality traits, rounded down. During the time this power is active the subject gains the Negative 
	Social trait \emph{Submissive}, and the caster cannot use this power on themselves. Though uncommon due to its casting time, 
	this ritual can be used to bring another kindred out of frenzy as well, though in such cases this ritual has no other effects. \\

	\item[Purify Blood] \emph{(Tremere 57, Any)} \hfill \\
	This simple ritual, taking five minutes in total, purifies one trait of human or animal blood against impurities, including 
	alcohol, drugs, and even some diseases, at Storyteller discretion.  This ritual requires that the blood be held in a copper 
	bowl, combined with ash and crushed ginger.  Blood affected by \emph{Quietus}, \emph{Vicissitude}, or similar powers cannot 
	be cleansed, and all purified blood tastes stale and flavorless. The success or failure of this ritual is immediately 
	evident in the color of the resulting mix. \\
	
	\item[Purity of Flesh] \emph{(Night 128, Any)} \hfill \\
	This ritual mystically purges poisons and drugs from a target's system, though not diseases or magical effects, distilling 
	them into a single trait of their blood which is drawn out of them by way of a golden needle.  The blood is putrid and likely 
	to cause great infection and upset to anyone imbibing it, depending on the amount of ailments removed and at Storyteller 
	discretion.  This power will not cure Flaws such as \emph{Disease Carrier} but may suppress their effects for an evening. \\

	\item[Rebirth of Mortal Vanity] \emph{(ST 67, A4)} \hfill \\
	This ritual allows a kindred to effectively grow hair.  For every inch of hair they wish, the recipient of the ritual, which 
	can be the caster, must pluck a hair from the head of a living child.  The thaumaturge then places the hairs on a mirror and 
	invokes the ritual, which absorbs the hair into the mirror itself.  For each hair used in the ritual the subject's hair will 
	grow one inch, staying at its new length until cut.  This power has no effect on bald vampires. \\

	\item[Rite of Introduction] \emph{(ST 68, Any)} \hfill \\
	Most often used for newly-arriving Tremere to announce themselves to a Domain's regent, the caster boils a handful of ground 
	tamarisk root in a pot of rainwater, then recites an incantation over the steaming vapors as they add a drop of galangal oil.  
	If successful they can speak a brief, thirty-second message of introduction which is sent to the highest-ranking local Tremere.  
	The recipient can reply telepathically for five minutes if desired.  All Tremere characters who begin play with at least one 
	dot of \emph{Thaumaturgy} receive this ritual for free. \\

	\item[Ritual's Recognition] \emph{(Tremere 59, Any)} \hfill \\
	The success or failure of a ritual is not always immediately apparent, possibly causing embarrassment or great danger for the 
	thaumaturge.  By casting this ritual first, requiring the severing of the caster's earlobe or tip of the nose (causing one 
	unsoakable Bashing wound) to be ground with mortar and pestle, the success or failure of the immediate subsequent ritual is 
	immediately known to the caster. \\

	\item[Rotten Wood] \emph{(Grey, non-Camarilla)} \hfill \\
	By spending twenty minutes at the beginning of an evening chewing through a one-inch piece of hardwood, without supernatural 
	strength to aid you, this ritual provides the caster the unique ability to warp and twist wood with a mere touch and moment of 
	concentration, until dawn.  Touch a wooden object and make a Static Mental challenge against a difficulty set by the Storyteller, 
	determined by the size of the object to be destroyed.  If used during combat this action takes a full turn to enact. \\

	\item[Sanguineous Phial] \emph{(ST 68, A5)} \hfill \\
	Mystically enchanting a vessel to preserve blood, the caster must obtain an earthenware jar and bury it for at least two full 
	nights, after which time it is dug up and an ash leaf is crumbled inside. At any point in that evening blood may be poured in, 
	the jar closed, and sealed with the tallow from a candle.  This jar, which must be represented by an item card, will keep its 
	sanguine contents fresh so long as it remains closed.  If opened the blood will spoil regularly, but if the vessel is destroyed 
	or broken it will spoil instantly.  This ritual must be cast each time the thaumaturge wishes to store blood, even if reusing 
	the same container. \\

	\item[Scent of the Lupine's Passing] \emph{(LotN 186)} \hfill \\
	With a mixture of milkweed, wolfsbane, and other herbs you can make a poultice that, when carried with you, allows you to 
	detect Werewolves by smell.  Make a Static Mental Challenge against all individuals within 10' of you to determine if any are 
	lupines.  Retest with \emph{Occult}. \\
	
	\item[The Scribe] \emph{(ST 68, A4)} \hfill \\
	After casting this ritual, any words the caster speaks for the remainder of the scene, or until desired, will appear into a 
	written document, which must be prepared ahead of time.  The translation is literal and in the caster's own handwriting.  
	The resulting document is permanent, as if the caster had written it themselves.  Large amounts of information may not easily 
	or cleanly fit on small target documents. \\

	\item[Sense the Mystical] \emph{(ST 68, A5)} \hfill \\
	Allowing the caster to sense magical effects and enchanted objects, they must chant for five full minutes while lighting a 
	candle that they then hold in their hand.  When the candlelight touches an object touched by, created through, or under the 
	effect of blood magic the item glitters, an effect visible only to the caster.  This power does not distinguish between 
	\emph{Thaumauturgy}, \emph{Necromancy}, or other blood sorceries, but will not trigger on normal Disciplines.  The candlelight 
	does not provide clues as to what kind of effect is in effect, just that one exists. \\

	\item[Serenading the Kami] \emph{(BM 91, A5)} \hfill \\
	Spending half an hour in quiet contemplation with incense and bathing in bull's blood, the ritualist gains the temporary aid of 
	spirits Eastern philosophers call ``kami.''  The caster gains a +2 trait bonus on the next Physical challenge they engage in after 
	this ritual succeeds.  Relenting to a challenge does not trigger this ritual's effects, which end at sunrise if not used. \\

	\item[Steps of the Terrified] \emph{(BM 93, A5)} \hfill \\
	This power was developed as a defense against those with \emph{Celerity} or other methods to outpace the Tremere. The caster must 
	spend ten minutes preparing this ritual before confronting the target, at which point they must spend three full turns casting 
	poplar buds, dousing their hands in oil, and repeating a short incantation three times.  If the target has not left the immediate 
	scene before the ritual is complete, they may only take a maximum of one step per combat turn, even if they use \emph{Celerity}, 
	for the remainder of the night. \\

	\item[Summon Guardian Spirit] \emph{(???, Any)} \hfill \\
	This power allows the thaumaturge to summon a spirit that is bound to warn the caster of danger until the next dusk.  Requiring 
	mystical symbols to be created using the ashes of a dead mortal during the casting, the spirit becomes visible to the summoner a 
	split second before danger rises, preventing them from being surprised in combat, and ensuring that they wake at the first sign of 
	danger during the day without a challenge. \\

	\item[Trima] \emph{(ST 69, A5)} \hfill \\
	A special concoction first created by those studying the Path of Dionysis, this beverage makes its imbiber drowsy and content, often 
	used to help facilitate feeding.  To create this ritual the caster must add one trait of their own vitae to wine, up to one cask's 
	worth, which causes all who drink it to suffer the Negative traits \emph{Submissive} and \emph{Lethargic} for the rest of the night, 
	as well as later forgetting specific details about the evening. The power of this ritual prevents the blood from causing the Blood 
	Bond in either mortal or kindred participants, though vampires can drink the liquid without difficulty.  At sunrise the wine 
	reverts to its normal, unaltered state. \\

	\item[Wake with Evening's Freshness] \emph{(LotN 186, A3)} \hfill \\
	By spreading the fresh ashes of bird feathers over your sleeping place, this ritual will allow you to wake from slumber at the first 
	sign of danger, suffering no penalties for actions taken during daylight for the first three turns afterward. \\

	\item[Ward Versus Mortals] \emph{(SD, A4)} \hfill \\
	As \emph{Ward Versus Ghouls} save this power targets regular mortals. \\
	
	\item[Ward Versus Ghouls] \emph{(LotN 186, A4)} \hfill \\
	By infusing your blood into an object you make its touch or presence disturbing and even painful to Ghouls, who suffer a Lethal 
	wound if they touch or are touched by it, in addition to any damage otherwise inflicted in combat.  The ward becomes active the 
	night following this ritual's casting, and can affect any single object from the size of a dagger to a large door.  The caster of this 
	ritual sacrifices a permanent blood trait which cannot be recovered until the ward breaks, either through destruction of the 
	item or the ritual being unwoven.  By adding the blood of any specific ghoul into the casting, that individual will be made 
	immune to its effects.  Anyone who would be affected by this ritual standing in conversational distance of a warded item 
	receives a free Static Mental Challenge against 5 traits, retested with \emph{Awareness}, to know that there is danger present.  
	This knowledge is automatic if attempting to interact with the warded object or if attention is drawn to it. \\

	\item[Whispers of the Ghost] \emph{(ST 69, A4)} \hfill \\
	By carrying the ear of a still-living creature in their left hand as they cast this ritual and subsequently use 
	\emph{Psychic Projection}, a Thaumaturge may speak into the physical world while out of their body for one scene, counted from 
	the time they first start speaking. \\

	\item[Will o' the Wisp] \emph{(Grey, Non-Camarilla)} \hfill \\
	This simple power, requiring a small willow branch and a five minute casting time, creates a small, softly-glowing ball of light 
	that floats near the caster for the next hour.  The ball can be commanded to glow more brightly, dim itself, divide into two 
	balls, bathe someone in its glow, fly to any point visible to the caster, or remain stationary.  The ball winks out of 
	existence if the caster ever leaves the immediate area without the ball following. \\

\end{description}

\subsubsection{Intermediate Rituals}
All Intermediate rituals have a static difficulty of 7 traits and a casting time of 20 minutes unless otherwise stated.  
A character wishing to learn an Intermediate ritual must first have at least Intermediate \emph{Thaumaturgy}. \\

\begin{description}

	\item[Bladed Hands] \emph{(Elysium 82, A4)} \hfill \\
	Requiring a blood trait and two whetstones, this ritual hones and reforms the caster's hands into weapons, granting them a +1 
	bonus trait in \emph{Brawl} challenges and making all such attacks inflict Lethal damage.  Due to the change fine dexterity 
	is difficult, resulting in a -1 trait penalty for such challenges at Storyteller discretion.  Anyone you touch with your 
	changed digits or who has clear sight of them will instantly notice that something is wrong. \\

	\item[Blood Allergy] \emph{(ST 69, A6)} \hfill \\
	A vicious curse for one's enemy, this ritual requires mixing a trait of the subject's vitae with dead rose petals.  If the 
	ritual succeeds, the undead victim cannot keep more than three traits of blood in their system until dawn, spending a full 
	turn vomiting for each extra trait that is in or enters their system.  It is very likely that this drastic reduction in 
	blood pool will force a hunger frenzy check at Storyteller discretion, even if the body cannot hold more vitae.  This power 
	has no effect on those kindred who have more dots of the \emph{Age} Background than the caster. \\

	\item[Blood Cert\'{a}men] \emph{(Tremere 61, R1)} \hfill \\
	The foundation of Clan Tremere's powers lie in the rituals and mystical knowledge of ancient mortal wizards, the traditions 
	of whom have shaped the Clan's history and future.  Blood Cert\'{a}men exists as one of the oldest forms of dispute resolution 
	between Tremere, though it is all but forgotten in modern nights.  The ritual opens with formal declaration of challenge, 
	and both contenders entering a circle of blood or vitreous humor no larger than ten paces across.  Once inside, the ability 
	to harness the raw energies of Thaumaturgy itself will decide the victor.  This power is largely based in cinematic 
	role-play but this ritual's entry in Clanbook Tremere should be referenced for specific mechanics and thematics used in our 
	game. \\

	\item[Bone of Lies] \emph{(LotN 186, A6)} \hfill \\
	Enchant a mortal finger bone at least 10 years old to bind its mortal spirit into it, requiring at least 10 traits of blood.  
	If the holder of the bone knowingly lies, the bone compels them to instantly reveal the truth and darkens noticeably.  
	This effect lasts until every trait of vitae is used up, one per lie, after which time the bone becomes black, withered, and 
	useless, the spirit inside it twisted by lies. Casting this ritual is a level 5 Humanity sin. \\

	\item[Bottled Voice] \emph{(???, A4)} \hfill \\
	This ritual mystically enchants a glass bottle which will hold the voice of the first person who speaks directly into it.  
	The thaumaturge must seal the bottle with wax immediately after it is so primed, after which point the victim can no longer 
	speak words or sounds of any kind.  The bottle remains so enchanted for the rest of the evening or until destroyed, 
	whichever comes first. \\

	\item[Cleansing of the Flesh] \emph{(ST 69, A4)} \hfill \\
	With the spread of blood-born illnesses, Clan Tremere has discovered ways to ensure that they are not carriers of such 
	diseases.  By spending a full night submerged in a bathtub or cauldron filled with purified water, they bleed all but the 
	tiniest drop of blood from their system, with all of the associated dangers of being low on blood.  If the ritual 
	succeeds, any non-supernatural diseases and foreign substances such as alcohol or narcotics are purged from their system.  
	This ritual may be performed on another kindred, who must be submerged and open their own veins as the thaumaturge chants  
	over them all night. \\

	\item[Craft Dream Catcher] \emph{(ST 70, A4)} \hfill \\
	Most commonly found among those studying the path of \emph{Oneiromancy}, the caster creates a portal into the target's 
	dreams and helps guard them against hostile spirits.  A Dream Catcher is an intensely personal talisman composed of the 
	target's hair, spittle, blood, and other sympathetic links.  The object's owner, who must keep it in their haven, cause 
	any hostile spirits to suffer a two-trait penalty on ties when trying to affect them, and may find that the effects of 
	such Flaws as \emph{Nightmares} are reduced.  The Oneiromancer who crafted the Dream Catcher has a two-trait bonus when 
	using \emph{Oneiromancy} against the subject, while other Oneiromancers suffer a two-trait penalty.  This power may be 
	used on oneself but in all cases requires the expenditure of a permanent blood trait which cannot be recovered unless
	the totem is destroyed or ritual unwoven. \\

	\item[The Curse Belated] \emph{(ST 70, A5)} \hfill \\
	Devised as a way to protect the interests of Clan Tremere, the caster permanently sacrifices a blood trait in the creation 
	of a brand with which he marks a ghoul.  If in future the ghoul dies they will reawaken as kindred 10 minutes later, as the
	childe of the caster, whose blood point is then returned, their brand vanishing in the process.  This safeguard even works 
	if someone else attempts to embrace the ghoul, though particularly violent or horrific deaths may result in the new kindred 
	earning the Flaw \emph{Permanent Wound} or a similar drawback. This power remains active until triggered. \\
	
	\item[Eyes of the Past] \emph{(Elysium 83, A5)} \hfill \\
	By expending two Mental traits and a Willpower while concentrating into a hand mirror or bowl of still, reflective water, this 
	ritual allows the thaumaturge to view their current surroundings at a specific time and date within the past five years for five 
	minutes.  This full-sensory experience requires the caster's full concentration, making them completely unaware of their physical 
	surroundings unless disturbed, incapable of moving, using Disciplines, speaking, or interacting with the world at all while the 
	ritual is in effect.  The area observed is equivalent to an average room, at Storyteller discretion.  The caster cannot use other 
	powers or Abilities to heighten their examination of the past, including attempts to pierce the powers of \emph{Obfuscate} in use 
	during the observed period. \\

	\item[Fire in the Blood] \emph{(Grey, non-Camarilla)} \hfill \\
	This ritual causes a victim to be wounded by their own aggressive natures.  The caster spends twenty minutes slowly burning an 
	effigy of the target made with at least one trait of the victim's blood, causing the caster one Aggravated wound.  The caster 
	must then touch the target, skin to skin, requiring a Physical challenge, while whispering or speaking the word “burn” aloud.  
	If successful any offensive Physical challenges entered into by the victim will result in a Lethal wound suffered before the 
	challenge is thrown as they feel great heat and pain welling up from within them.  This power has no effect on vampires in 
	frenzy. \\

	\item[Flesh of Fiery Touch] \emph{(Elysium 83, A4)} \hfill \\
	By spending two hours in a meditative trance and then swallowing a burning ember, causing one Aggravated wound, the caster's 
	skin takes on a rich bronze hue as it becomes a deadly weapon until the next nightfall.  While this ritual is active any who 
	initiate skin to skin contact with the caster suffers one Aggravated wound per touch or turn of continued contact.  This power 
	may not be used offensively, as it relies on the victim initiating contact. \\

	\item[Gentle Mind] \emph{(Elysium 83, A3)} \hfill \\
	A ritual with many inherent dangers, it nevertheless provides a subject with a valuable defense against the beast -- two 
	temporary Willpower traits, only available to resist frenzy for the rest of the week.  The caster and the subject exchange one 
	trait of blood each while chewing wolfsbane to complete this ritual.  No thaumaturge can cast this ritual on themselves. \\

	\item[Heart of Stone] \emph{(Elysium 83, A4)} \hfill \\
	By lying prone in the center of an earthen circle at least three inches high and six feet in diameter arranged atop a natural 
	stone surface for one hour with a lit candle on their chest, a thaumaturge may harden their heart against attempts to stake them.  
	As the candle burns down it deals one unsoakable Aggravated wound, but if successful the caster cannot be staked by any means 
	until the ritual ends, either by their own choice or at the end of one story, which ever comes first.  Hardening one's heart in 
	this manner forces the sacrifice of all \emph{Friendly} and \emph{Compassionate} Social traits, which cannot be recovered until 
	after the ritual's end, and grants the caster \emph{Callous x3}.  While active the caster cannot spend Willpower. \\

	\item[Haunted House] \emph{(Elysium 83, A5)} \hfill \\
	This ritual must be cast on a location where a kindred has slept for at least one week in the current story. By anointing the 
	corners of the property with a total of four blood traits and burying or hiding a broken child's toy somewhere on the premises 
	mortals will soon consider the location creepy and haunted, as if the location itself possessed a type of \emph{Eerie Presence}, 
	an effect that lasts for one year.  Some consider this ritual to be a breach of the Masquerade while others see it as an extension 
	of an already superstitious and credulous world. \\

	\item[Illusion of Peaceful Death] \emph{(Elysium 84)} \hfill \\
	By brushing a corpse with the feathers of a dove, then leaving them on scene, this ritual heals visible wounds on a corpse, making 
	it appear as if the person died of natural causes.  It does not add blood to a body, but will remove reasons for the coroner to 
	check for blood loss.  The body must have at least half of its natural blood pool for the ritual to succeed. \\

	\item[Incorporeal Passage] \emph{(LotN 186, A4)} \hfill \\
	Stare into a hand-sized piece of mirror while casting this ritual.  Once complete you become completely immune to physical barriers 
	and forces, including attacks, but can only walk directly forward or stand still, without turning.  Lasting one scene or hour, 
	you can end the ritual early by turning the mirror away.  Ending this ritual while partially or wholly inside solid objects 
	yields damage as determined by the Storytellers. \\

	\item[Infirm Inert] \emph{(ST 70, A7)} \hfill \\
	One of the most devastating rituals in Clan Tremere's arsenal, this power prevents the victim from utilizing one of the kindred 
	body's most valuable abilities -- healing.  By drinking blood laced with laudanum, granting themselves \emph{Lethargic} for the 
	rest of the evening, the caster preps the ritual, which is completed by smearing a small amount of their own blood on the target.  
	Once so applied, the victim cannot spend Blood to heal, though this restriction can be suppressed for one turn by spending a 
	Willpower trait.  When this ritual expires the victim may heal as normal. \\

	\item[Inherited Affinity] \emph{(Tremere 59, A6)} \hfill \\
	An excruciating ritual which subjects a target to physical and magical torture, undergoing this rite nevertheless greatly decreases 
	the time required to learn to properly wield \emph{Thaumaturgy} from decades to scant weeks.  The caster must have uninterrupted 
	access to the subject for an entire night, during which time the subject is commonly chained to a wall or table.  They are drained 
	of all but one blood trait and six golden needles are inserted into chakras of power, though each Thaumaturge has their own method, 
	causing five unsoakable Lethal wounds. The subject must drink a terrible concoction of rendered fat and bile to complete the ritual.  
	From a mechanics perspective, any character wishing to learn \emph{Thaumaturgy} must undergo this ritual, and it is assumed that all 
	Tremere characters have, shortly after their embrace.  Anyone subject to this ritual is likely to frenzy due to the blood loss and torture. \\

	\item[Innocence of the Child's Heart] \emph{(Elysium 84, A5)} \hfill \\
	Hiding your true thoughts from the power of \emph{Aura Perception}, while this ritual is active your aura reads as a brilliant white, 
	purely innocent and wholesome.  A toy stolen from a child must be destroyed and the remnants carried on the caster's person for this 
	ritual to be effective.  For each Mental trait sacrificed before casting the ritual, minimum of one, this ritual lasts one hour. \\
	
	\item[Inscription] \emph{(Tremere 58, A5)} \hfill \\
	Occasionally the needs of House and Clan require that a Tremere cast a ritual in which they themselves are not proficient.  
	This ritual allows any Basic ritual to be inscribed upon a sheet of paper, able to be cast by anyone who possesses the 
	Discipline of Thaumaturgy.  Inscribed rituals are imperfect and so cannot be used to learn new powers. This ritual takes 
	20 minutes plus the normal casting time of the rite to be inscribed, and the inscription lasts one story.  Both the creator 
	of the inscription and the caster must pay all costs associated with the ritual and provide all material components  
	required, the former when inscribing, the latter when casting. \\

	\item[Iron Mind] \emph{(Grey, non-Camarilla)} \hfill \\
	By spending twenty minutes concentrating on a cold iron circlet, the caster may thereafter walk without fear of intrusion into their 
	mind, so long as they wear the band on their head.  If another character attempts to engage the thaumaturge with any \emph{Auspex} 
	powers for the remainder of the evening, they are informed that to do so they must spend a Willpower before engaging in the 
	challenge.  No character may be forced to spend more than one Willpower in an evening to overcome this power. \\

	\item[Keening of the Banshee] \emph{(???, A5)} \hfill \\
	By enchanting a pendant carved from a tombstone at least one-hundred years old, this ritual allows the thaumaturge to utter a 
	single horrific scream which has devastating effects on the nearest mortal, aging them a full ten years and turning their hair 
	shock white.  Mortals who are already of advanced age may die from this assault.  If unused the pendant crumbles at dawn. \\

	\item[Mark of Amaranth] \emph{(Tremere 63, A6)} \hfill \\
	A debilitating and often fatal curse, this ritual ensures that a target reads as having committed diablerie to the powers of 
	\emph{Aura Perception} and \emph{Blood Walk} until sunrise.  The thaumaturge must posses an item of great value of the intended 
	target and place that object inside a vampire the caster slays as the material component of this ritual.  The target has no idea 
	that they are so marked, but their ``sins'' are clear to any who look. \\

	\item[Major Creation] \emph{(ST 81, A5)} \hfill \\
	Only useful to those studying the \emph{Path of Conjuring}, this ritual expands the Conjurer's ability to create large items.  
	By spending a Willpower trait and severing their own thumb, the thaumaturge may now spend two or three Mental Traits 
	to make a summoned item either double or triple its normal size, though the complexity of the object to be created is still 
	limited by the specific \emph{Path of Conjuring} power being utilized.  This ritual expires after the creation of one object 
	or dawn, whichever comes first, and causes two unsoakable Lethal wounds in the casting. \\

	\item[Mirror Walk] \emph{(???, A4)} \hfill \\
	By pressing a ring bearing an emerald against a mirror large enough to crawl through, this ritual allows a thaumaturge, and up 
	to one passenger if desired, to use mirrors as a means of transportation.  The traveler(s) emerge out of the nearest mirror 
	large enough to fit through.  If no such mirror is available, as determined by the Storytellers, they emerge out of the nearest 
	pane of glass large enough to suffice.  The mirror and glass take on a rippling water effect during the transfer. \\

	\item[One Mind of the Convens] \emph{(SD, R1)} \hfill \\
	An invaluable tool for the coordination of efforts, this ritual acts as a more powerful version of \emph{Rite of Introduction}, 
	linking the Regent either to other Regents in the local area or to the Lord, as desired. \\

	\item[Pavis of Foul Presence] \emph{(LotN 187, A5)} \hfill \\
	A powerful secret of the Tremere Clan, by enchanting a blue silken cord that is worn around the neck you become immune to 
	\emph{Presence} until the ritual ends.  This power reflects the next successful \emph{Presence} Challenge affecting you back 
	against its user, automatically succeeding as if you had used the power instead.  This snaps the cord, ending the ritual.  
	Relenting to a \emph{Presence} power or being subject to a power without a challenge does not invoke this ritual. \\

	\item[Power of the Pyramid] \emph{(Tremere 60)} \hfill \\
	Perhaps forming the basis of the many mystical feats ascribed to the Tremere, this ritual allows multiple kindred to share 
	Willpower from one communal pool.  Each Tremere in the casting must know this ritual, fast for a full twenty-four hours 
	beforehand, and link hands, with one of the thaumaturges wearing a broach made of human bone piercing their skin.  Casting 
	the ritual as one, when the ritual has completed a single Tremere may leave the circle and go about the rest of their 
	evening, able to use the combined pool of Willpower from every participating caster as if it were their own, subject to the 
	normal restrictions of Willpower use.  If any other member of the group breaks contact, the ritual ends immediately. \\

	\item[Protean Curse] \emph{(Elysium 84, A5)} \hfill \\
	After successfully casting this ritual, requiring pungent herbs and a full trait of blood taken from a rabid vampire bat, any 
	human or vampire who drinks the concoction is forced into the shape of a bat until dawn, with the appropriate advantages and 
	disadvantages present in the Protean power \emph{Shape of the Beast}.  Forcing someone to drink this potion may require 
	multiple Physical challenges. \\

	\item[Recure of the Homeland] \emph{(Grey, non-Camarilla)} \hfill \\
	This powerful ritual allows the thaumaturge to heal their own Aggravated wounds incredibly quickly.  By spending an hour in silent 
	meditation, holding up to two handfuls of soil from their mortal home town, then placing the dirt on their wounds, up to two 
	Aggravated wounds may be healed without further cost.  The use of this power blackens and corrupts the dirt, making it unusable 
	for future applications.  This power may not be used more than once per week. \\

	\item[Rend the Mind] \emph{(BM 96, A6)} \hfill \\
	Clan Tremere has learned how to attack not just the body of their enemies but also the mind within.  After spending a full hour 
	in meditation, consuming the brain of a rabid animal, the caster may at any point in the remainder of the evening make a 
	single Contested Mental challenge against someone they can see, retested with \emph{Occult}.  If successful the thaumaturge 
	inflicts three Bashing wounds against the target, though by sacrificing up to three Mental traits before the challenge the 
	damage is increased one Bashing per trait.  Kindred subjects halve all Bashing damage as normal, rounding up. \\

	\item[Rending Sweet Earth] \emph{(Elysium 84)} \hfill \\
	Used by historic Tremere to root out Gangrel, this ritual which has the caster whip the natural earth with a leather whip violently 
	disturbs an area of natural earth, approximately a cube ten feet to a side.  If cast in a location where a kindred is currently 
	using \emph{Earth Meld}, a successful Contested Mental challenge will force the hidden creature to the surface, fully aware of 
	their surroundings.  If the submerged kindred is in torpor this challenge automatically succeeds. \\

	\item[Respect of the Animals] \emph{(???, Any)} \hfill \\
	By meditating on a patch of natural earth for thirty minutes this power grants the caster the Merit \emph{Inoffensive to Animals} 
	for a period of four hours after the ritual's completion. \\

	\item[Return of the Heart] \emph{(ST 71, A6)} \hfill \\
	Usually only possessed by those studying the \emph{Path of the Blood's Curse}, this power forces complete, unrelenting guilt 
	upon its target.  By mixing a trait of the victim's blood with the tears of an infant, the thaumaturge forces the victim to 
	reflect upon their past actions through the eyes of an innocent.  While this does not affect a permanent Morality path rating, 
	for the rest of the evening the subject behaves as if they had a Humanity rating of 10, regardless of their normal Morality path 
	or rating.  This power is highly role-play dependent. \\

	\item[Rutor's Hands] \emph{(LotN 187, A3)} \hfill \\
	This ritual constructs a tiny servant out of your own hand and eyeball, causing you to suffer five unsoakable Aggravated wounds 
	which must be healed before the ritual can be used again.  Through a mental link you see and hear everything the creature 
	experiences, directed by your mental commands, though it slumbers through the day as you do.  This creation is permanent, 
	though it must be fed one trait of blood, from any source, each week or it crumbles to dust.  The construct has only 1 health 
	level and three Stamina-related Physical traits; it has no offensive ability.  In creating this assistant the caster permanently 
	sacrifices a blood point which cannot be recovered until the creation dies or the ritual is unwoven. \\

	\item[Scry] \emph{(ST 71, A4)} \hfill \\
	Causing a still body of water, whether natural or artificial, to become a Scrying pool requires owl's blood.  The caster may then 
	concentrate either on a location or a person to view.  If a location they must have physically traveled there themselves, and if 
	a person they must possess an object of personal significance to the target.  Neither \emph{Auspex} nor other powers may be used 
	through the Scrying pool, no sound is transmitted, and the caster cannot change the target of the ritual once cast.  This power 
	lasts for ten minutes after casting, though the viewing time may be lengthened by the expenditure of one Mental trait 
	at the time of casting for each additional ten minute period, to a maximum of 30 minutes. \\

	\item[Shaft of Belated Quiescence] \emph{(Cam TT 112, A5)} \hfill \\
	This ritual enchants a specially-prepared stake into an even more potent weapon against other kindred.  Requiring five hours to 
	cast, the stake must be made of rowan wood, coated with three traits of the caster's blood, and blackened in an oak-wood fire.  
	After this enchantment is completed the stake is mystically active for the remainder of the story.  If the caster successfully 
	strikes someone with the stake and does not successfully pierce the heart, the tip of the stake breaks off and begins burrowing 
	through the target's system, ending the ritual for the remaining stake shaft and likely rendering it ill-suited for further staking 
	attempts.  This process is quickly fatal to mortals, but for every hour thereafter the Storytellers will throw two simple tests 
	with the victim.  If the victim loses both, they become instantly staked.  Attempts to dig out the stake may only be made once 
	per hour and are likely to result in Lethal wounds to the subject, at Storyteller discretion.  Only impaling weapons made of 
	wood can be so enchanted. \\

	\item[Soul of the Homunculus] \emph{(LotN 187, A4)} \hfill \\
	Requiring at least one hour of attention each night for a full story to succeed, this ritual creates a tiny replica of the caster, 
	completely loyal to their needs.  It can resemble a small winged creature capable of flight, a legless slug, or a small 
	marmoset-like creature.  Whatever the form, it always bears the caster's face.  Homunculi have three Stamina-related Physical 
	traits and two health levels, with no offensive ability.  You can only have one homunculus at any one time. \\

	\item[Splinter Servant] \emph{(Cam TT 113, A5)} \hfill \\
	Designed to aid the Tremere in immobilizing its enemies, this ritual enchants a stake carved from a tree which has nourished 
	itself on the dead, bound in wax-sealed nightshade twine.  When the binding is torn off, requiring a single action, the 
	splinter servant leaps to life, animating itself and attempting to stake a target directed by the caster.  If working in 
	concert with the thaumaturge the servant acts as an NPC assistant, granting +1 trait in the comparison of ties, otherwise it 
	has 4 Physical traits and two offensive combat retests.  The servant is only animated for five turns, starting with the turn 
	after its activation, but is incredibly hardy -- any attempt to remove the stake once it has impaled its victim requires a 
	Dexterity-based Static Physical challenge against 7 traits or pieces of the stake remain in the heart even after the main shaft 
	is pulled, requiring additional digging to remove completely, potentially inflicting further wounds at Storyteller discretion.  
	An unused splinter servant collapses into dust at the end of the story. \\

	\item[Stolen Kisses] \emph{(ST 71)} \hfill \\
	By making a small incision on their body with a thistle steeped in vampiric vitae, the caster seals the wound into an undetectable 
	mouth-like sucker which only opens when pressed against a mortal's warm flesh, draining one trait of Blood every other turn.  This 
	type of feeding does not cause the Kiss nor any immediate discomfort to the victim, other than the usual penalties for having lost 
	blood.  The mouth remains until sunrise. \\

	\item[Telecommunication] \emph{(ST 72, A4)} \hfill \\
	Not all rituals are steeped in tradition; some Warlocks are finding themselves at home in the modern era.  This power affects any 
	television the caster has touched within the past week.  Dropping into a meditative trance the caster may get a television's-eye-view 
	into the target room for ten minutes after the completion of the ritual, though additional Mental traits may then be spent to increase 
	the duration by ten minutes each, to a maximum of five.  During this time they may regulate any images or sounds the television generates, 
	from changing the channel to crafting a fake broadcast (which may require a \emph{Performance} or \emph{Expression} Ability test).  
	During the meditation the caster cannot initiate any other challenges and if their concentration is broken the ritual ends immediately. \\

	\item[A Touch of Nightshade] \emph{(ST 72, A6)} \hfill \\
	This ritual allows the caster to target a single victim, greatly harming kindred and likely killing mortals.  Anointing their hands 
	with the bitter extract of the nightshade plant, which seeps undetectably into the skin, the next creature or person they touch with 
	a bare hand contracts a terrible poison which cannot be healed by mortal medicine, causing one Lethal damage per hour to mortals or 
	one Bashing damage per hour to kindred.  There is no way to reverse this poison; once a target has been exposed it must run its 
	course until sunrise. \\

	\item[Track Transgressor] \emph{(ST 72, A4)} \hfill \\
	Developed as a means for Tremere to track down those outsiders who may possess Thaumaturgy, the caster spills one trait of their 
	own vitae on the ground where the perpetrator is thought to have cast magic in the past twenty-four hours.  If successful the 
	caster can follow that individual for the rest of the evening, tracing the exact path they took after leaving the area where magic 
	was worked.  This ritual only tracks those who have cast Thaumaturgy, not Necromancy or any other kind of blood magic.  In the 
	event of multiple workings, the Storyteller will decide which path(s) are revealed. \\

	\item[Transubstantiation of Seven] \emph{(Tremere 61, A7)} \hfill \\
	Cast as part of the embrace of every Tremere, this ritual transforms the caster's vitae, placed into a large chalice or bowl and 
	imbibed by the target, into a mix of the Tremere Council's blood, forever linking the initiate with the pyramid.  This ritual 
	is also used as punishment, strengthening the bond of the Clan over one of its members who has started to stray.  Such power is 
	contained within this ritual that the bond between subject and Clan Tremere will never fade, unlike all other Blood Bonds.  Other 
	uses of this power exist for the purposes of casting Chantry-specific rituals in a process known only to Regents. \\

	\item[Unweave Ritual] \emph{(Tremere 64, A5)} \hfill \\
	At times an ongoing ritual becomes a problem for Clan Tremere, and it becomes necessary to remove it.  The caster must be under 
	the effects or in the presence of the ritual to be unwoven and possess the material components required to cast the original 
	spell.  After casting this ritual, engage in a Contested Mental Challenge against the original caster, though you receive a 
	+2 bonus in the event of a tie if you yourself also know the ritual.  If successful the ritual ends and you suffer any effects 
	triggered by the end of the ritual, if any.  Note that magical effects created through paths of \emph{Thaumaturgy} cannot be unwoven, 
	this power only affects rituals described in this volume. \\

	\item[Ward Versus Fae] \emph{(SD, A4)} \hfill \\
	As \emph{Ward Versus Ghouls} save this power targets the creatures of Faerie in all of their forms. \\

	\item[Ward Versus Kindred] \emph{(SD, A5)} \hfill \\
	As \emph{Ward Versus Ghouls} save this power targets vampires. \\

	\item[Ward Versus Lupines] \emph{(SD, A4)} \hfill \\
	As \emph{Ward Versus Ghouls} save this power targets werewolves. \\

	\item[The Watcher] \emph{(Elysium 85, A4)} \hfill \\
	An amalgamation of \emph{Auspex} and \emph{Animalism}, this power enchants a rat to go to a specific location the caster directs 
	and look for a specific object, person, or situation.  When the rat returns the caster may touch its head and see what the rat 
	has seen on its journey.  For the rat to understand the commands the caster must succeed in a Static Social challenge, retest 
	with \emph{Animal Ken}, with a difficulty set by the Storyteller.  The rat is still subject to powers of \emph{Animalism} while 
	on its journey. \\
	
\end{description}

\subsubsection{Advanced Rituals}
All Advanced rituals have a static difficulty of 9 traits and a casting time of 30 minutes unless otherwise stated.  
A character wishing to learn an Advanced ritual must first have Advanced \emph{Thaumaturgy}. \\

% MARK -- replace " (" with "] \emph{(" and ")" with ") \hfill \\" -- watch for parentheses inside the text though

\begin{description}

	\item[Abandon the Fetters] \emph{(Tremere 65, R2)} \hfill \\
	One of the most secret rituals within Clan Tremere, this power allows the caster to shatter blood bonds in the subject.  
	If knowledge that such capability were even possible ever made it outside the Clan it could bring ruin to all Tremere; 
	only high Apprentices are even aware of this ritual's existence.  This ritual is excruciating for both caster and subject, 
	the latter of whom must be restrained, and requiring great quantities of vitae.  The caster must completely exsanguinate 
	the target, mixing the blood with one trait of the regnant's and five of their own in a large glass basin.  After bringing 
	the subject to the point of death (Incapacitated with at least Lethal damage) over the course of an entire evening the 
	caster shatters the bowl, breaking the bond with it.  The subject suffers the loss of one permanent Willpower trait and at 
	least four of their current wounds get upgraded to Aggravated.  The caster suffers one unsoakable Aggravated wound.  This 
	power even removes the supernatural connections formed through the ritual \emph{Transubstantiation of Seven} or the Sabbat 
	\emph{valuderie}. \\

	\item[Blood Contract] \emph{(LotN 187, A6)} \hfill \\
	By spending three full nights in the writing of a contract in your own blood, you create an unbreakable compact between 
	yourself and one signatory.  An additional blood trait must be spent by both signers to sign the document, the literal and 
	specific terms of which are immutable.  Should either party break any term of the contract, that individual immediately 
	suffers enough Aggravated wounds to place them in Torpor.  The only other ways to finish the contract are to fulfill its 
	terms or physically burn it.  Any contract must be written out as an item card, reviewed by the Storytellers, signed by both 
	players, and kept on file. \\

	\item[Cobra's Favor] \emph{(ST 73, A5)} \hfill \\
	This ritual was created to prevent anyone from risking diablerie against a Tremere.  After combining one trait of their own 
	blood with a brew of toxic herbs and snake venom, the caster then recites a complicated incantation over it, calling upon 
	the spirit of all things baneful.  After this the concoction turns a fetid black and the ritualist must ingest the elixir, 
	suffering one unsoakable Aggravated wound in the processes.  If the ritual succeeds, the thaumaturge's blood turns into a 
	deadly poison and deals one level of Aggravated damage per trait to anyone imbibing it for one full story.  Needless to say 
	this ritual makes creating ghouls or childer impossible. \\

	\item[Court of Hallowed Truth] \emph{(ST 73, A6)} \hfill \\
	Originally created for Tremere tribunals, this ritual has seen wider use in service to Princes who worry about their populace.  
	By placing a pair of crossed bones before every door and window to a room, the caster weaves a powerful magic that prevents 
	any falsehood from being spoken within the room, no matter how damning.  Direct questions from the presiding judge or 
	authority must be answered completely and candidly, with no creative omissions.  This power lasts for one full night.  Princes 
	who rely too heavily upon this power both find themselves deeply indebted to the Tremere and hated by the Domain's residents. \\

	\item[Curse of Clytemnestra] \emph{(Elysium 85, A5)} \hfill \\
	Invoking the power of ancient gods you are able to destroy one male mortal or ghoul by aging him rapidly, decaying him into dust.  
	This ritual takes one full evening to cast and requires a lyre at least 100 years old, a personal possession of the victim, and 
	at least one trait of their vitae.  At dawn the target makes a Static Physical challenge against the caster's Physical traits, 
	bolstered by one for each trait of the victim's blood they drank during the casting of the ritual.  If the victim fails they are 
	utterly destroyed, but even if they win they are incapacitated with Lethal damage, and likely to suffer permanent wounds even after 
	they heal. \\

	\item[Dominion] \emph{(???, A6)} \hfill \\
	By placing specific iron seals above all doors to a moderately-sized room, after a three-hour casting time this ritual prevents any 
	use of \emph{Animalism, Auspex, Dominate}, or \emph{Presence} initiated inside the room by anyone except the caster.  This power 
	secures the room for one full week. \\

	\item[Enchant Talisman] \emph{(???, A5)} \hfill \\
	By sacrificing a permanent blood trait into a mystical focus, the caster can gain a significant boost to their magical abilities.  
	When attempting to cast \emph{Thaumaturgy} with the focus wielded prominently in one hand, they gain a +3 bonus on ties.  For powers 
	which require physical contact this bonus only applies to the Mental challenge for the actual casting, not the initial grab.  This 
	artifact is no more sturdy than normal and its power is dismissed if broken. \\
	
	\item[Mindcrawler] \emph{(???, A6)} \hfill \\
	By painting a mystical sigil upon a small tick, dyed red, then crushed upon the victim's forehead at the conclusion of this 
	ritual's casting, this power eats away the target's mental faculties over time.  Each successive night the victim loses 
	one Mental trait, randomly determined, which will not recover normally the following evening.  This process continues until 
	the victim is left with one trait, at which point the ritual ceases and the victim starts to recover traits again, randomly 
	determined, one per night until the entire power has passed its course. \\

	\item[Nectar of the Bitter Rose] \emph{(LotN 187, R1)} \hfill \\
	This most secret of powers allows multiple people to share in the fruits of diablerie.  By restraining the victim and casting 
	this ritual over them, five characters (no more, no less) must throw a Simple Challenge.  If a character wins or ties, they 
	receive all benefits and drawbacks of the diablerie as normal. \\

	\item[Night of the Red Heart] \emph{(Tremere 65, A7)} \hfill \\
	This power allows Tremere to exact revenge or punishment on others from great distances, provided certain conditions are met.  
	The caster must have carved an effigy of the target either out of bone and rotten wood harvested at midnight, or stone from 
	a faithful priest's headstone, as well as at least one trait of the target's blood, and spend a Willpower to begin the ritual.  
	The casting of this ritual takes all night, from dusk until dawn.  Over the next half hour the victim feels a great feeling of 
	dread -- a strong pull that they must leave the Domain by sunrise or they will die, but will also come to realize the identity, 
	general direction, and general distance of the caster, who must be within the same Domain.  The subject recognizes that, if 
	they wish to survive the night, they must either leave the Domain or kill the caster before sunrise.  If at dawn the target 
	is out of the Domain or the caster slain, the ritual has no effect.  If however the target is still inside the Domain, they 
	are killed, reduced to ash in an instant.  In extreme situations this ritual is sometimes used to keep hopelessly captive 
	Tremere from revealing Clan secrets. \\

	\item[Paper Flesh] \emph{(???, R1)} \hfill \\
	One of the most devastating powers in the Tremere's arsenal, this ritual, requiring one trait of the victim's blood, strips away 
	the protective effects of \emph{Fortitude}.  After the two-hour casting time completes, the subject finds they no longer have 
	access to any but the Basic levels of \emph{Fortitude} for the remainder of the night.  The target instantly knows that something 
	is wrong, and that they feel weaker, less stable than normal, but remain ignorant of the true effects of this ritual until their 
	supernatural toughness unexpectedly fails them. \\

	\item[Severed Hand] \emph{(ST 73, A6)} \hfill \\
	Developed during the dark ages for use by despotic Princes, this ritual causes wounds to become permanent, forever a part of 
	the victim's existence.  By spending an entire evening swabbing a severed appendage, including arms, hands, eyes, feet, or 
	legs, as well as the stump with volatile and mysterious compounds, the caster ensures that the kindred becomes permanently 
	maimed, receiving a Flaw appropriate to their situation such as \emph{One Arm, Bad Sight, Lame}, et cetera.  There is no 
	known way of healing this maiming naturally once the ritual completes, though the physical wound levels are healed normally.  
	This ritual can be undone through \emph{Unweave Ritual}, allowing the subject to start regrowing the appendage as normal. \\

	\item[Stone of the True Form] \emph{(ST 74, A6)} \hfill \\
	This ritual forces any form-altering creature back into its natural state.  By coating a small pebble in one trait of their 
	vitae, the caster creates a talisman capable of rendering even enraged werewolves unable to shape-shift.  The creation of 
	this stone costs the caster a permanent blood trait which cannot be recovered until the ritual completes through use.  To 
	finish the ritual the caster must touch the stone to a creature with the ability of transformation, normally requiring a 
	touch-based Physical challenge.  If successful the ritual completes, forcing the creature back into its natural shape and 
	preventing it from changing for one scene or hour.  This ritual completely neuters the transformative powers of \emph{Protean}, 
	\emph{Serpentis, Vicissitude}, and other similar powers, as well as select mental powers such as \emph{Obfuscate}. \\

	\item[Stone Slumber] \emph{(ST 74, A5)} \hfill \\
	This ritual allows a caster to sleep away the day in relative safety, even when the environment provides no cover from the sun.  
	Beginning exactly one hour before sunrise the thaumaturge smears their body with the blood of a twelve hour-old corpse.  Then, 
	standing still in an open area and facing East, if the ritual succeeded the light of the sun will instead turn the caster to 
	stone, completely protected from all forms of physical damage short of complete destruction.  The caster will wake ten minutes 
	after sunset, though doing so requires an additional Blood trait above the normal cost for waking.  If the ritual has failed 
	the kindred is very likely to meet Final Death in the sun's unrelenting rays. \\

	\item[Thirst Unquenchable] \emph{(Grey, non-Camarilla)} \hfill \\
	By spending five minutes sprinkling salt around the victim, the target spends the rest of the evening feeling as if they were 
	starving, no matter how much blood they consume.  This ritual almost always leads to frenzy at the first sign of provocation 
	or opportunity to feed, per the rules for having a low blood pool.  This power may be used on mortals, who ceaselessly gorge 
	themselves on any available food. \\

	\item[Umbra Walk] \emph{(LotN 188, A5)} \hfill \\
	Through the power of this ritual, requiring the sacrifice of an intelligent being (a Humanity 4 sin), you may travel to the 
	uncharted lands of the umbra, realm of spirits and gateway to strange worlds.  Additional individuals may accompany you, at 
	the cost of a fresh sacrifice per person, with all involved throwing for Morality as relevant.  You arrive naked though certain 
	magical items may accompany you at Storyteller discretion.  You may explore this dangerous plane for as long as desired, exiting 
	at any time by concentrating for three full terms or by finding your entrance point.  The contents and scenarios present within 
	the Umbra are wholly at the discretion of the Storytellers. \\

	\item[Vires Acquirit Eundo] \emph{(BM 98, A4)} \hfill \\
	By reciting an elaborate incantation and breaking an hourglass, casting the sand over a green flame, the immediate subsequent 
	ritual the caster performs has an extended or improved effect, completely at the discretion of the Storyteller. \\

	\item[Ward Versus Wraiths] \emph{(SD, A4)} \hfill \\
	As \emph{Ward Versus Ghouls} save this power targets the creatures of spirit in all of their forms, including entities using 
	powers such as \emph{Psychic Projection}. \\

\end{description}