\section{Practitioners of Magic}
\label{sec:clans}
All throughout kindred history rumors have surfaced about strange abilities attributed 
to specific Clans, powers shrouded in mystery and unavailable to any other Blood.  The 
Clans who have managed to develop these impressive Disciplines are few and far between, 
and guard their secrets with the utmost ferocity, taking exacting and sometimes fatal 
vengeance against those who pry too deeply.

Across the whole of kindred kind there are only three Clans who can claim to have control 
over Thaumaturgy, and only one that can call themselves masters of Necromancy.  Rare 
cases of small or historic bloodlines being able to wield these powers have been known, 
but their numbers are so few or so far in the past as to put them out of the thoughts of 
all but the most meticulous of kindred scholars.

Each Clan's sourcebook has great information about the history, culture, and internal 
structure of the Clan and their outlook on kindred existence.  The information presented 
below is meant to be an overview or supplement to the works already published by 
White Wolf.

\subsection{Clan Tremere}
\label{sec:tremere}
The undisputed masters of Thaumaturgy, Clan Tremere claims that they alone developed 
the rites and rituals required to bend the very fabric of reality to their whims.  
Almost invisible to those outside the Clan, a rigid and well-established hierarchy 
controls almost all aspects of a Tremere's study of Thaumaturgy and interactions with 
others who share their blood.  Groups of Tremere are organized into Chantries, usually 
no more than one per metropolitan area.  A great deal of competition takes place 
between the members of a Chantry, each fighting for recognition and promotion within 
the Clan structure, called ``the Pyramid,'' but when faced with an external threat the 
Clan unites as one well-organized and unstoppable force.

\subsubsection{Organization}
At the lowest level, and most relevant to the characters of \emph{Sanguine Dreams}, are 
the \textbf{Apprentices}.  Each Chantry is made up of Apprentices, who are designated 
according to their ability and benefit to the Clan.  Ranked from the first to the seventh 
``Circle of Mystery,'' most player-characters will fall between the ranks of A3 and A6.  
Note that rank has very little to do with kindred age or experience, and just as at times 
characters will be elevated, so too may they be demoted if they earn their superiors' 
displeasure.  As an Apprentice moves up in Rank, they are given more responsibility but 
also greater access to powers and areas of study.

Apprentices of the First and Second Circles of Mystery are functionally under Accounting, 
unable to leave the Chantry or the presence of a higher-ranking Tremere for any reason.  
Once an initiate has demonstrated a proper command over Thaumaturgy and knowledge of 
kindred society are they raised to the Third Circle.

Apprentices of the Third, Fourth, and Fifth Circles serve as the backbone of Clan Tremere, 
with increasing responsibilities and research opportunities.  These kindred have proven a 
basic competency of Thaumaturgy and have shown their value to the Clan as a whole.  Very 
often the Primogen, as public face of the Clan, comes from these ranks as higher-level 
Apprentices are too busy to take on such outward-facing responsibility.

Apprentices of the Sixth and Seventh have proven themselves highly proficient not only in 
their mastery of Thaumaturgical power but also individual specializations therein, often 
fulfilling a specific niche unavailable to other kindred.  The highest-ranking Apprentice 
in a Chantry, almost always at this level, is called the ``High Apprentice'' and it is 
often their responsibility to oversee the education of less experienced magi, even if 
not directly.

Each Chantry is lead by a \textbf{Regent} who serves as master of the house.  Just as 
there is functionally no appeal if a kindred dislikes their Prince, there is almost no 
ability to go over a Regent's head when it comes to the conduct or management of a Chantry.  
These kindred, also ranked from the First to the Seventh Circles, have vast stores of both 
knowledge and power and have at least a base understanding of all aspects of Thaumaturgy, 
including the mastery of rituals required to create, maintain, and defend a Chantry.  Often 
a Regent's rank is directly related to the size or importance of the Chantry over which they 
are called to preside, but such is not a universal rule.

Each Regent reports to a \textbf{Lord} who oversees large geographical areas and the 
management of each chantry therein.  These beings are as far above Regents as Regents are to 
Apprentices, their power and understanding of the mystic arts almost unfathomable to younger 
kindred.  When a Regent issues a directive, it can be said to come from the Lord's will.  When 
a Lord issues a directive, it can be said to come from the very Clan itself.

There are higher levels of the Tremere hierarchy, but even the most effective Apprentice has 
scarce more than a whisper's chance of meeting someone in those lofty positions unless they 
have made a series of truly regrettable decisions.

The Clan has codified a strict hierarchy of which paths and rituals can be studied, depending 
an Apprentice's Circle of Mystery rank.  It is unlikely that most have even heard of powers 
more than two ranks above their own, but local conditions and needs sometimes force 
Regents to authorize otherwise undeserving kindred to learn the secrets of their betters.

\subsubsection{Common Powers}
Every Tremere begins their life as a student of \emph{Thaumaturgy} with the study of the \emph{Path of Blood}, 
from which the core of the Clan's power stems.  As they grow and advance many who are more 
combat-oriented learn \emph{Lure of Flames} or \emph{Movement of the Mind} while others 
take a more esoteric role, studying \emph{Spirit Manipulation} or \emph{Oneiromancy}.

Clan Tremere has the largest collection of paths and rituals available to them, and have the 
easiest time learning them of all the thaumaturgically-active Clans, its internal hierarchy notwithstanding.


\subsection{Clan Assamite}
\label{sec:assamite}
Description of Clan Assamite and its history (the curse, Alamut, taking contracts, et cetera)

\subsubsection{Organization}
Talk about the types of Assamites (particularly how we only allow the actual assassins as PCs, 
not Viziers or others) and their roles here

\subsubsection{Common Powers}
Discuss paths of Thaumaturgy "common" to select Assamites and what they do to share powers.  
Discuss the rituals available/limited to them.


\subsection{The Followers of Set}
\label{sec:settite}

\subsubsection{Organization}

\subsubsection{Common Powers}


\subsection{Clan Giovanni}
\label{sec:giovanni}

\subsubsection{Organization}

\subsubsection{Common Powers}
