\section{Abilities}
\label{sec:abilities}
Abilities represent knowledge or skills that your character has learned through 
hard work, careful study, and repetition.  Acting as retests for challenges and 
limitations on what your character can accomplish in a given situation, Abilities 
are some of the most-used elements on a character sheet. 

Rated from zero to five, each dot represents increasing aptitude in a given area.  
One dot would represent enough skill that your character could arguably make a 
living, such as a small-time mechanic having one dot of \emph{Repair}.  Only truly 
gifted visionaries might ever achieve four or five dots in an Ability, let alone rate 
highly in several. While the mechanics for each Ability are presented below, possessing 
dots represents understanding and competency in the Ability as a whole, and not strictly 
just within the realm of challenges.

Here is the complete list for Abilities available to Camarilla kindred in 
\emph{Sanguine Dreams}.  Other Abilities may exist in rare and unique situations, 
as determined by the Storytellers.  Some abilities such as Crafts or Science must be 
focused; \emph{Crafts: Pottery} is a different skill from \emph{Crafts: Blacksmithing} 
and so forth.

Abilities are most often used as retests in challenges (see Chapter~\ref{sec:challenges}) 
and also help determine whether or not a character can attempt a given task, based on 
their experience and knowledge; some challenges may not be possible for characters to 
attempt if they do not possess specific skills, such as picking locks or hacking computers.  \\

\begin{description}
	\item[Academics:]  Represents scholastic education and may aid in obscure general knowledge.  One dot 
	represents a Bachelor's degree while five is the equivalent of multiple PhDs, a true master of your field. 
	Often soft sciences are represented as Specializations of this Ability.
	\item[Animal Ken:]  The ability to relate to or train animals and primary retest for Animalism.
	\item[Athletics:]  The appropriate retest for raw physical actions like running, climbing, or jumping.  
	Also the primary retest for thrown weapons.
	\item[Awareness:]  You have honed your sensitivity to the supernatural energies around you.  By spending an 
	Awareness when a power fails in your presence you may gain a static Mental challenge against the power's user.  
	Success reveals only that a power was attempted but not which power or by whom.  You may retest this challenge by  
	spending another Awareness.
	\item[Brawl:]  The primary retest for grappling and attacking while unarmed.
	\item[Computer:]  Used when dealing with advanced electronics.
	\item[Crafts:]  Represents the physical or mechanical perfection of a specific artistic medium.  This Ability 
	must be focused for a particular art form. The time to craft objects depends greatly on both the complexity of 
	the item being created and the skill of the maker.  See a Storyteller for more details regarding a desired project.
	\item[Dodge:]  The appropriate retest when avoiding danger via Dexterity-based traits when one is aware of the attack and can move; one cannot Dodge if they are caught unawares.
	\item[Drive:]  Skill at advanced vehicular maneuvers.
	\item[Empathy:]  By spending an Empathy and winning a Social Challenge against a mortal you may determine if 
	the last thing they said was a lie.  The same test and cost may be used to determine anyone's Demeanor.  This 
	Ability also serves as the primary retest for Dementation.
	\item[Etiquette:]  Spending an Etiquette may help avoid social gaffes in high society situations.
	\item[Expression:]  This Ability represents the emotional content of a specific artistic medium, and must 
	be focused appropriately.
	\item[Finance:]  By spending a level of Finance you receive a windfall of \$250 delivered to your haven, usable 
	once per week per dot.
	\item[Firearms:]  Allows the use of Mental traits when firing a gun and is the primary retest thereof.  Note that Celerity 
	cannot be used to augment such Mental challenges.
	\item[Hunting:]  Representing a character's skill at finding sustenance it also adds to a character's starting 
	blood pool each gather.
	\item[Intimidation:]  Primary retest for Dominate or when lording over others.
	\item[Investigation:]  Primary retest for Auspex and when making a dedicated search of an area.
	\item[Law:]  Knowledge of mortal law and its intricacies.
	\item[Linguistics:]  Each dot allows for one additional fluent spoken and written language, which must be 
	specified on your character sheet.
	\item[Lore:]  This Ability represents the chance you possess rare or secret knowledge about the supernatural 
	that you wouldn't otherwise have obtained, at Storyteller discretion. It is normally assumed that a character 
	knows enough about their Clan, kindred nature, and the Camarilla to pass their Accounting and be Acknowledged.  
	Those kindred with \emph{Age} are presumed to have gathered even more information in their years of experience.  
	Lores are most commonly focused into Clan-based, Sect-based, or regarding kindred nature, and all uses of \emph{Lore} 
	should be addressed to the Storytellers.
	\item[Medicine:]  Used in healing mortals under your care.
	\item[Melee:]  Primary retest for all attacks with a hand-held, close-range weapon.
	\item[Occult:]  Primary retest for Thaumaturgy and Necromancy, and represents general knowledge of the arcane.
	\item[Performance:]  Represents the display of physical exertion in an artistic way.  Must be focused, often 
	into Dance, Singing, or Acting.
	\item[Politics:]  By spending a Politics you may learn a kindred's Status, and perhaps some of their history at Storyteller fiat, such as where they were most recently Acknowledged.
	\item[Repair:]  Knowledge of machinery and how to fix it in an emergency.
	\item[Science:]  Represents knowledge of a physical laboratory science and its application.  Must be focused 
	into a specific academic discipline such as Botany or Chemistry.
	\item[Scrounge:]  A successful Static Mental challenge may yield miscellaneous equipment or single-use tools.
	\item[Security:]  Knowledge of practical intrusion countermeasures and how to bypass them.
	\item[Stealth:]  Primary retest for Obfuscate.  For slipping though an area unnoticed without the aid of 
	Disciplines, engage in a Mental versus Physical challenge, provided you have cover and opportunity.
	\item[Streetwise:]  As \emph{Etiquette} for lower-class groups or situations.
	\item[Subterfuge:]  Retest for Serpentis.  By spending a Subterfuge and winning a Social Challenge after a conversation you may determine one of someone's relevant Negative Social traits (their choice).
	\item[Survival:]  The primary retest when resisting damage through Stamina traits, this Ability may also 
	aid in finding shelter from the rising sun.
\end{description}

\subsection{Additional Rules}

\begin{itemize}
	\item Spent Abilities refresh one dot per Ability per evening upon waking.
	\item Only one Ability may be purchased to level 5 per character.
	\item Most Abilities may be specialized once for 2xp (e.g. \emph{Firearms: Light Pistols} or \emph{Politics: 
	City Government}), provided you have at least two dots of the Ability.  Specializations grant +1 trait 
	on tie resolution when their narrow focus is applicable.  This bonus is only available when you have dots 
	of the Ability remaining unspent, and you must declare if you are applying a specialization to a challenge 
	before it is thrown. Specializations cannot be used in conjunction with Merits in challenges.  Nor can 
	Specializations apply to an entire Discipline, but may apply to certain powers in specific circumstances, 
	at Storyteller discretion.
\end{itemize}
