\section{Thirteen Clans}
\label{sec:clans}
Though other bloodlines and offshoots exist, vampire culture on the whole 
recognizes thirteen distinct Clans, each descended from antiquity.  Often 
defined by their Disciplines, or vampiric powers, each Clan tends to 
gravitate toward particular stereotypes or archetypes, though whether that 
is due to selection of similar-thinking kindred or something inherent in the 
blood is the subject of much debate among kindred scholars.

\subsection{The Camarilla}
Usually displaying a civil and rational countenance, the Clans making up the 
Camarilla have long stood together against the might of their enemies.  
Espousing a dedication to the ideals of humanity, reason, and propriety, 
the truly wise among them recognize that they are every bit as vicious and 
bloodthirsty as their enemies, even if expressed in differing ways.

\subsubsection{Brujah}
Fiery and passionate, the Brujah are a force to be reckoned with both socially 
and physically.  While many appear to be no more than street thugs and punks, 
many hold onto the Clan's more historic ideals of strategy and planning, becoming 
well-respected tacticians and leaders.  Brujah are often found holding martial 
positions such as Scourge and Sheriff. \\

\textbf{Role-playing Hints:} More than any other Clan, Brujah are ruled by their 
passions.  Play up the struggle to maintain your self-control in the face of 
external pressures.  Remember that not every Brujah is a slobbering combat monkey 
and that there are many other sides of the stereotype to play.

\textbf{Disciplines:}  Celerity, Potence, Presence

\textbf{Advantage:}  All Brujah characters begin with a free \emph{Political}, 
\emph{University}, or \emph{Street} Influence as well as the corresponding 
Ability of \emph{Politics}, \emph{Academics}, or \emph{Streetwise}, owing to 
their connections to the fields of revolution across the globe.  In addition 
Brujah can often count on their brethren coming to their aid when necessary, 
this ``call to arms'' uniting an otherwise often fractious Clan of passionate 
believers.

\textbf{Disadvantage:}  So closely tied are they to their passions Brujah often 
have difficulty reining in their Beast.  You suffer a one-trait penalty on all 
Self-Control or Instinct Virtue tests (see Chapter~\ref{sec:morality}).

\subsubsection{Gangrel}
Loners and survivalists, Gangrel often have a fierce attachment to nature and 
evenings spent under the star-decked canopy of bare sky.  Territorial, they take 
their role as protectors of city boundaries seriously, but of late have had to 
remind the rest of the Camarilla of their worth. \\

\textbf{Role-playing Hints:} A difficult balance exists between trying to play a 
loner and contributing to a social game like \emph{Sanguine Dreams}.  Think not 
only about what makes a Gangrel different from other kindred but also what makes 
them the same.  They are fierce but compassionate, driven yet tempered.  Think of 
their place within the greater kindred society, both on the outskirts and on the 
forefront.

\textbf{Disciplines:}  Animalism, Fortitude, Protean

\textbf{Advantage:}  Gangrel are often nomadic, at home in the wilds between 
oases of civilization.  The Camarilla tends to give Gangrel wider permission to 
roam and explore the outlands than their more urban cousins, rarely enforcing 
any bans to their movements.  All Gangrel gain a free level of the \emph{Animal Ken} 
and \emph{Survival} Abilities as well.

\textbf{Disadvantage:}  Closer to nature than any other Clan, whenever a Gangrel 
frenzies she gains an animalistic feature.  Future frenzies cause additional 
features or existing ones to become more pronounced.  Every time a Gangrel 
frenzies during the chronicle they gain the Negative Trait \emph{Bestial}, 
\emph{Feral}, or \emph{Repugnant}, up to five total, which cannot be bought off.

\subsubsection{Malkavians}
Varied and mercurial, Malkavians are possessors of great insight and terrible 
madness, though some claim they are one and the same.  Researchers, miscreants, 
oracles, and a few genuine sociopaths, most Malkavians are focused on discovering 
the truth of reality and sharing it with all who would listen. \\

\textbf{Role-playing Hints:} Cuddly-bunny Malkavians are almost universally slain 
by their sires---think about the deeper, darker side of madness, the altered 
perceptions that truly give these kindred a different, greater, understanding of 
the world at large.  Remember that no derangement is taken lightly and all will 
form the lens through which your character views the world.

\textbf{Disciplines:}  Auspex, Dominate, Obfuscate

\textbf{Advantage:}  Uniquely connected to the chaotic underpinnings of reality, 
every Malkavian receives a free dot of the \emph{Awareness} Ability.  In addition 
their frequent insight makes their outbursts and mistakes easier to stomach at 
court---once per story a Malkavian may ignore another's Status without cost or 
repercussion for one outburst or challenge.

\textbf{Disadvantage:}  Every member of Clan Malkavian is clinically and 
certifiably insane.  These disorders are not humorous and form a core of the 
vampire's being.  Each Malkavian must choose a Derangement which can never be 
fully cured.

\subsubsection{Nosferatu}
Twisted and deformed by their embrace, Nosferatu are luckily blessed with the 
power to hide their appearance from prying mortal eyes.  This supernatural 
talent has made them the perfect information gatherers and secrets remain their 
stock and trade to this night.  Often found as Scourges or Seneschals, they 
work invisibly to ensure the success of their own Clan, and through them the 
Camarilla at large. \\

\textbf{Role-playing Hints:}  Whether playing a martyr, a Cleopatra, or any 
other archetype, remember that your transformation has made you a social 
pariah, having to hide yourself just to exist.  And yet you may wear your 
disfigurement proudly, for you are reminded nightly of your curse while others 
strive their entire unlives to hide and forget theirs.  Cynicism is an almost 
universal trait among this Clan.

\textbf{Disciplines:}  Animalism, Obfuscate, Potence

\textbf{Advantage:}  Trained from embrace in the arts of skulking and hiding, 
every Nosferatu begins play with a bonus level of the \emph{Stealth} and 
\emph{Survival} Abilities.

\textbf{Disadvantage:}  The embrace horribly twists and deforms all Nosferatu, 
often in ways that would make other kindred retch.  Their very undisguised 
appearance is a threat to the Masquerade.  No Nosferatu may possess the Social 
traits \emph{Alluring}, \emph{Gorgeous}, or \emph{Seductive}.  In addition they 
receive the Negative Traits \emph{Repugnant x3}, which do not provide Free Traits 
and may never be removed.  A Nosferatu whose normal visage is apparent may not make 
non-intimidating Social challenges.

\subsubsection{Toreador}
Social elitists, Toreador are often found in the most public of offices, serving as 
Harpies, Keepers of Elysium, and Princes as they maintain the social order.  
Often passionate about art and culture, they themselves are usually artists or 
patrons thereof.  Catty and prone to infighting, the Clan can nevertheless make 
or break someone's reputation and so are often treated with a great deal of 
respect. \\

\textbf{Role-playing Hints:}  Nobody knows how best to navigate the social order 
like you; pay careful attention to Status (page~\pageref{sec:status}) and how best 
to wield it.  Work on spreading awareness of culture and propriety to the uneducated 
kindred masses.  Be better than everyone else, because you are better than everyone 
else.

\textbf{Disciplines:}  Auspex, Celerity, Presence

\textbf{Advantage:}  Owing to their usual artistic backgrounds each Toreador 
enters play with the \emph{Academics}, \emph{Crafts}, \emph{Performance}, or \emph{Subterfuge} 
Abilities, one dot of any two or two dots of one.  A Toreador can also call 
on their artistic endeavors to feed, using these selfsame Abilities as if they 
were points of the \emph{Herd} Background when necessary at game.

\textbf{Disadvantage:}  Easily entranced by true beauty, when presented with a true 
masterpiece (as determined by a Storyteller) Toreador fall into a deep trance of 
reflection and awe.  Only by spending a Mental Trait or being jostled can break 
them of this reverie.

\subsubsection{Tremere}
Holding an uncertain but powerful role withing the Camarilla, few Tremere are truly 
trusted even in the loosest scope of the term.  Their magics mark them as powerful 
but also dangerous, and they often find that suspicion and doubt follow their every 
step. \\

\textbf{Role-playing Hints:}  Rule \#1 is to read the Tremere Oath.  Read it before 
every game and follow it to the letter.  The Oath and internal Clan structure are 
what have kept the Tremere from being destroyed in the many wars since their 
inception.  Know your place within the Clan and what is expected of you for advancement.

\textbf{Additional Notes:}  Almost without exception Tremere PCs will enter play 
between Rank A3 and A5.  All such characters will receive \emph{Rite of Introduction} 
at no cost.

\textbf{Disciplines:}  Auspex, Dominate, Thaumaturgy

\textbf{Advantage:}  Being trained in the mystical arts, all Tremere begin play 
with one free \emph{Occult} Ability and \emph{Occult} Influence.  In addition all 
requests for the aid of a Mentor will be met as if the player tied on the challenge.

\textbf{Disadvantage:}  All Tremere are permanently one step blood bound to the Clan's 
highest-ranking members, and all failings are dealt with harshly.  There is no room 
for mistakes within the pyramid.

\subsubsection{Ventrue}
The self-imposed and undisputed elite of kindred society, Clan Ventrue has an 
unshakable sense of Clan superiority.  Architects of the Camarilla itself, they 
seek to rule the night from positions of power across the world.  More so than 
any other Clan, Ventrue pride themselves on the specifics of their lineage, and 
great care is taken to prove themselves worthy of the noble blood bestowed them. \\

\textbf{Role-playing Hints:}  You are the rightful voice of tradition in any 
Domain.  Be vigilant against threats to the social order but know that your place 
is at the top, where you can lead with strength and determination, and by example.  
Think of how anachronistic your character may be, owing to the long accounting and 
tutelage required for all Ventrue.  When reading the Clanbook pay particular 
attention to the organization of the Board of Directors.

\textbf{Disciplines:}  Dominate, Fortitude, Presence

\textbf{Advantage:}  Due to their keen financial sense all Ventrue possess an 
extra trait of the \emph{Resources} Background that can never be lost.  Additionally 
they possess one level of \emph{Finance}, \emph{High-Society}, or \emph{Political} 
Influence.  Because Clan Ventrue puts such a high premium on the lineage from which 
they descend, it is almost impossible to infiltrate the Clan.

\textbf{Disadvantage:}  All Ventrue have selective tastes, unable to gain 
sustainment from any prey not meeting their exacting standards.  They possess 
the ``Selective Digestion'' Flaw for no traits, though it only penalizes them 
one point for the purpose of starting blood pool.

\subsection{The Sabbat}
A frightening and zealous religious order, the Sabbat is a mystery to most 
Camarilla kindred.  Known for their campaigns of violence and destruction 
across all corners of the Earth, they seem to have little regard for the 
polite and social trappings of the Camarilla, particularly the rules regarding 
progeny and destruction.  They have declared an unending war against the 
Camarilla and its elders, and are a constant external threat for Domains 
across the globe.

\subsubsection{Lasombra}
Unquestioned rulers of the Sabbat, the Lasombra have guided the ever-growing 
Sect since its inception.  While it is almost unheard of for a Lasombra to 
be allied with another Sect, exceptions do happen, descending from potent 
bloodlines that have always been loyal to the Camarilla. \\

\textbf{Role-playing Hints:}  As an anti-tribu you recognize that the whole 
of your Clan wishes your death before all others.  They see you as a turncoat 
and traitor, even though you have never walked among them.  You are wholly 
committed to the Camarilla, and see the proliferation of Sabbat Lasombra as 
a blight on your good family name.

\textbf{Disciplines:}  Dominate, Obtenebration, Potence

\textbf{Advantage:}  All Lasombra, whether Sabbat- or Camarilla-aligned are 
truly ``Respected'' for their contributions and leadership, and as such receive 
that extra positive patronage, which may never be permanently lost.  
Maintaining their connection to the church as they have since the Dark Ages, 
all Lasombra receive one free \emph{Church} Influence for free.

\textbf{Disadvantage:}  It is said that Lasombra do not possess souls, having 
traded them away for their command over darkness.  As such all Lasombra 
characters possess ``Casts No Reflection'' for no traits.  Owing to their 
affinity for darkness, all exposure to sunlight yields an extra level of 
damage per turn.

\subsubsection{Tzimisce}
Mysterious and alien, Tzimisce are truly the masters of form and function, 
twisting the human and kindred body to suit their dark experiments.  Included 
just for completeness' sake, there exist no record of any modern Tzimisce 
holding non-Sabbat affiliation, and as such are not suitable for play as PCs. \\

\textbf{Role-playing Hints:}  None as Tzimisce are not approved for play.

\textbf{Disciplines:}  Animalism, Auspex, Vicissitude

\textbf{Advantage:}  In addition to their vast stores of knowledge providing a 
free dot of the \emph{Occult} ability, Tzimisce characters may often learn the 
first two dots of any \emph{Lore} without a trainer or Mentor, at Storyteller 
discretion.  In addition they may have revenants as \emph{Retainers} which require 
no monthly blood upkeep and utilize specific rules found in \emph{Clanbook: Tzimisce}.

\textbf{Disadvantage:}  Possessed of a mystical tie to the lands of their 
ancestral birth, every night a Tzimisce spends away from at least two handfuls 
of their native soil imposes a cumulative -1 trait penalty on all non-Virtue challenges.  
These penalties are reduced by one for each night the Tzimisce again sleeps in the 
proper circumstance.

\subsubsection{The Anti-Tribu}
Almost every Clan holding membership within the Camarilla has had defectors 
migrate to the other side.  These anti-tribu normally possess the same 
temperament and powers as their Camarilla brethren, but in some extreme cases 
they have evolved or changed to be more than what they once were.  These 
Clans are not suitable as PCs.

\subsection{Independent Clans}
Not every Clan and bloodline has chosen a side in the three-prong war between 
the Anarchs, Camarilla, and Sabbat.  Some powerful lineages have remained 
independent from the beginning, marking them as powerful but untrustworthy 
allies whose motives are often their own.

\subsubsection{Assamites}
Cursed by the Tremere to never partake of kindred blood, once a staple of their 
insatiable diet, Clan Assamite has served as assassins to political leaders 
the world over.  Their methods are mysterious and their motives even more so, but 
it is of no doubt that they chafe under the yoke of Tremere magic. \\

\textbf{Role-playing Hints:}  As the appointed judge of all Cainites, yours is 
to know your targets and study them to make the moment of their death perfect.  
Take contracts only from Princes, and always, always receive payment in \emph{vitae}.  
The Assamite stronghold must be stockpiled, and your tithes help the wisest 
among you come closer to breaking the vile Curse that has been so unjustly 
put upon you.

\textbf{Disciplines:}  Celerity, Obfuscate, Quietus

\textbf{Advantage:}  Trained often from birth to be killers, all Assamites receive 
one \emph{Brawl} and one \emph{Melee} Ability at character creation.

\textbf{Disadvantage:}  Cursed to never imbibe kindred blood or commit diablerie, 
each point of kindred vitae you ingest inflicts one unsoakable Aggravated wound.  
Diablerie is all but impossible.

\subsubsection{Caitiff}
Those degenerates are too weak of either generation or vitae to express any traits 
normally associated with a specific Clan, forcing them to scratch out a living within 
or just outside the Camarilla hoping to gain some measure of protection from the evening's 
many other predators.  With no Clan to protect them, and no organization on their own, 
they are all alone in a world that is not kind to fledgling vampires with little guidance.  
The Elders fear and hate these thin-bloods, though they are often tight-lipped about why 
exactly. \\

\textbf{Role-playing Hints:}  Whether you choose to reveal yourself or not, you are 
at the absolute bottom of the pecking order, of every pecking order.  Your blood is 
weak and you have a difficult time mastering Disciplines, so make many deals to ensure 
your survival.  Be very afraid, and suck the marrow out of your potentially short life.

\textbf{Disciplines:}  Special, see below.

\textbf{Advantage:}  A Caitiff may learn any or all of the common eight Disciplines 
(Animalism, Auspex, Celerity, Dominate, Fortitude, Obfuscate, Potence, and Presence) 
without a teacher and for out-of-Clan cost.  They may never teach anyone a Discipline 
they have learned.

\textbf{Disadvantage:}  Being outcasts and disgraced, all Caitiff suffer the negative 
social stigma of being ``\emph{Caitiff}'' which goes over and beyond the normal limit for 
Negative Status, and which can never be removed.  In addition they may never learn the 
Advanced level of any Discipline without an appropriate teacher.  Caitiff characters are 
unlikely to begin play lower than 12th Generation.

\subsubsection{Followers of Set}
Viewed by many as corrupters and predators of the weak and unsteady, the Settites 
are unquestionably adept at fulfilling requests most other Clans couldn't bear to 
suggest.  They remain carefully neutral, even compared to other Independent Clans, 
and have managed to survive their many enemies' attempts to crush them by proving 
themselves invaluable, time and time again. \\

\textbf{Role-playing Hints:}  Neither the Paths of Ecstasy nor Typhon are easy to 
role-play but when done well they can be incredibly fulfilling.  Remember that your 
number one goal, above everything else, is to see your god risen from the grave as 
you yourself have been. None outside the Clan will serve him willingly, but they 
are weak and filled with frivolous desires.  Fulfill them, and gain more followers 
for his eventual return.

\textbf{Disciplines:}  Obfuscate, Presence, Serpentis

\textbf{Advantage:}  Focused on the weak and underhanded aspects of society, all 
Settites begin play with the \emph{Streetwise} Ability and one dot of \emph{Political}, 
\emph{Street}, or \emph{Underworld} Influence.

\textbf{Disadvantage:}  Just as Set was banished into darkness so have the 
Settites been.  Exposure to sunlight always yields one extra damage and bright lights 
of any kind, including spotlights, floodlamps, or flares impose a one-trait penalty 
on all challenges.

\subsubsection{Giovanni}
Both a family and a Clan, it seems every member is somehow related to one another 
through mortal ties.  A powerful and organized force whose motives aren't well-known 
nor -understood by outsiders, rumors have time and again held true that they have 
access to resources and secrets not available to normal, Camarilla, kindred.  All rules 
for Wraiths are found in the \emph{Crimson Terrors} supplemental packet. \\

\textbf{Role-playing Hints:}  Remember that you are an outsider but that you have 
the unique ability to get kindred what they need, even if they don't know what it is.  
Be secretive about your motives and your means, but always deliver on your promises.

\textbf{Disciplines:}  Dominate, Necromancy, Potence

\textbf{Advantage:}  Gain an automatic level in \emph{Finance} or \emph{Health Influence} 
and either a second dot in that Influence or a one-point wraith \emph{Retainer}.

\textbf{Disadvantage:}  There is no love within the Giovanni kiss.  All Giovanni 
possess the Flaw \emph{Grip of the Damned} for no points.  In addition each Blood trait 
taken from a mortal inflicts a level of Lethal damage to the victim.

\subsubsection{Ravnos}
An international band of thieves, tricksters, and charlatans, the Ravnos are often 
chased from one city to another when they overstay their welcome.  Members of this Clan 
seem incapable of controlling their predilections, resulting in more than one powerful 
kindred calling them a scourge on vampire-kind. \\

\textbf{Role-playing Hints:}  Think beyond the stereotypical gypsy 
kleptomaniac---the Ravnos have a rich history and motives behind everything they do and 
how they act.  You are a part of a noble and free heritage the likes of which no other 
kindred will ever understand, save perhaps your cousins in the Gangrel, even though they 
despise you for it.

\textbf{Disciplines:}  Animalism, Fortitude, Obfuscate

\textbf{Advantage:}  All Ravnos begin with one level of the \emph{Streetwise} Ability and 
one dot of \emph{Street} or \emph{Transportation} Influence.   Often their cons are so 
well-crafted that the victims would rather suffer than reveal they fell for the scheme, 
allowing the Ravnos to escape severe punishment.

\textbf{Disadvantage:}  Each Ravnos suffers a weakness of character linked to a 
particular crime, be it theft, murder, short-changing, or any number of swindles.  
When presented with an opportunity to indulge in the chosen vice a 
Self-Control/Instinct test (difficulty three) must be thrown to avoid taking advantage 
of the opportunity.

\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
\subsection{``Others''}
\addtocontents{toc}{\protect\setcounter{tocdepth}{2}}
While there are other, less populated bloodlines and small caches of secretive kindred 
throughout the world, they are not allowed for play or numerous enough to make a 
recurring appearance in \emph{Sanguine Dreams}.  The Storytellers can tell you more 
if you are interested in the finer points of their effect on kindred history.